---
title: "Deep learning for species distribution models"
author: "Austin M. Smith, Andrew M. Kramer, César Capinha"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.dim = c(8, 6), fig.align = 'center', echo = TRUE)
```

### Project Overview


Species distribution models (SDMs) have become indispensable tools for relating species occurrences to environmental conditions. Most commonly, these models utilize machine learning algorithms to statistically evaluate environmental covariates to determine the relative suitability of locations on the landscape (e.g., [Elith & Leathwick 2009](https://doi.org/10.1146/annurev.ecolsys.110308.120159)). Machine learning is a supervised learning framework; that is, models are fitted to training examples that consist of measured correlates and a desired output value ([Hastie et al. 2009](https://link.springer.com/book/10.1007/978-0-387-84858-7); [James et al. 2013](https://link.springer.com/content/pdf/10.1007/978-1-4614-7138-7.pdf); [Kuhn & Johnson 2013](https://link.springer.com/book/10.1007/978-1-4614-6849-3)). These models are then used in predicting the outcome of novel data. 

While these models are useful at estimating a species range, an extensive amount of literature exists pertaining to the limitations of SDMs (e.g., [Pearson & Dawson 2003]( https://doi.org/10.1046/j.1466-822X.2003.00042.x) ; [Hijmans 2012](https://doi.org/10.1890/11-0826.1); [Melanesi et al. 2019](https://doi.org/10.1002/ece3.5938) ; [Norberg et al. 2019]( https://doi.org/10.1002/ecm.1370)).  Currently these models are limited to static predictors, usually constructed from averaging climate data over extended periods. Deep learning neural networks (DLNN) have been used in other fields of research to interpret time series dynamics and can be used to fit SDMs without averaging or simplifying input data, and enable dynamic processes to better inform the models ([Capinha et al. 2021](https://doi.org/10.1016/j.ecoinf.2021.101252)).

The goal of our study was to expand on the findings in [Capinha et al. (2021)](https://doi.org/10.1016/j.ecoinf.2021.101252) by evaluating the predictive potential of time series deep learning models. We used 30 years of monthly bioclimatic data to predict species distribution for four previously studied, globally invasive species. We then compared four deep-learning architectures to three favored machine learning methods trained on 19 static predictors.

### Methods

#### Software

 We used a combination of R (https://www.r-project.org) and Python (https://www.python.org) for all of our data pre-processing, computations, and graphics. Our time series analysis was performed in Python with Keras (https://keras.io) and  TensorFlow (https://www.tensorflow.org) deep learning suites, and the time series analsyis package,  mcfly ([van Kuppevelt et al. 2020](https://doi.org/10.1016/j.softx.2020.100548)).  We used several R geospatial packages for traditional static modeling procedures (for an in depth tutorial of this, check the official R-Spatial [website](https://rspatial.org/raster/sdm/index.html)). 

```{r include=FALSE}

library(raster)
library(dismo)
library(maptools)
data(wrld_simpl)

source("./R/Functions.R")

boar =  read.csv( "./Data/data_raw/Sales_et_al_2017_boar.csv" )
parakeet = read.csv( "./Data/data_raw/Bohl_et_al_2019_parakeet.csv" )
kudzu = read.csv( "./Data/data_raw/Callen_and_miller_2015_kudzu.csv" )
ladybird = read.csv( "./Data/data_raw/Berdinger_et_al_2015_ladybird.csv" ) 

monkeyflower_train <- read.csv( "./Data/data_raw/Angert_et_al_2018_Monkeyflower_train.csv" )
monkeyflower_test <- read.csv( "./Data/data_raw/Angert_et_al_2018_Monkeyflower_test.csv" )

us_ext <- extent( -146.337891 , 17.182779 , -47.373047 , 55.850650 )
mf_ext <- extent( -125.156250 , 32.287133 , -110.917969 , 49.439557 )


```

#### Species data {.tabset .tabset-pills}

We used occurrence records from four previously published SDM studies pertaining to invasive species for our analysis:  Wild Boar (*Sus scrofa* ; [Sales et al. 2017](https://doi.org/10.1111/1365-2656.12721)), Kudzu (*Pueraria montana* ; [Callen & Miller 2015](https://doi.org/10.1111/ddi.12341)), Asian Harlequin ladybird (*Harmonia axyridis* ; [Bidinger et al. 2012](https://doi.org/10.1111/j.1439-0418.2010.01598.x)), and Monk Parakeet (*Myiopsitta monachus* ; [Bohl et al. 2019](https://doi.org/10.1111/jbi.13573)).

In addition to the global invasive models, we reviewed a study pertaining to scarlet monkeyflower (*Erythranthe cardinalis* ; [Angert et al. (2018)](https://doi.org/10.1086/695984)), a native plant to western California and Oregon, United Sates.  In this study, historical occurrences (n = 431) were collected for model training, pseudo-absences  were extracted from  donut-like buffers  with the center/occurrences removed, and tested using field records collected to validate model performance, and to evaluate habitat for potential range expansion. Note, the testing records consist of both presence and true-absences (e.g., P/A modeling). 

We replicated the methods used in [Angert et al. (2018)](https://doi.org/10.1086/695984) for creating our data set:

* Created donut-like buffers around each point ( outer radius = 80km ; inner radius = 600m ) 
* Collect random pseudo-absences from buffer( n = 1000 ). 
* Test models on validation dataset 

Here, the validation data provided consists for 240 observations: 96 presences; and 144 absences.

Ideally, SDMs are built using both presence and absence records; however, absences are often not recorded. A reasonable alternative is to use pseudo-absence or background points, which are data points pulled from areas assumed to be less suitable due to the lack of recorded occurrences (...).  We chose to use two spatial extents for our modeling procedure.  First, we randomly sampled 10,000 terrestrial background points from a global buffer. Next we chose to construct a 100KM buffer around our occurrence points and merged these polygons to create a reduced spatial extent/study region, and then sample an additional 10,000 background points. 



##### Boar 
```{r echo=FALSE}

#par(mfrow=c(2,2))
plot(wrld_simpl , main = "Wild Boar Occurrences", axes = TRUE, col= "light yellow")
points(boar$long , boar$lat, col = "red" )

```

##### Kudzu
```{r echo=FALSE}

plot(wrld_simpl , main = "Kudzu Occurrences", axes = TRUE, col="light yellow")
points(kudzu$long , kudzu$lat, col = "red" )
```

##### Ladybird
```{r echo=FALSE}

plot(wrld_simpl , main = "Ladybird Beetle Occurrences", axes = TRUE, col="light yellow")
points(ladybird $long , ladybird $lat, col = "red" )


```

##### Parakeet
```{r echo=FALSE}

plot(wrld_simpl , main = " Monk Parakeet Occurrences", axes = TRUE, col="light yellow")
points(parakeet$long , parakeet$lat, col = "red" )

```

##### Monkeyflower
```{r echo=FALSE}

mf_circles <- circles( monkeyflower_train , d = 80000, dissolve=TRUE , lonlat=TRUE )

plot( wrld_simpl , main = " Monkeyflower  Occurrences", axes = TRUE, col="light yellow" , xlim = c( -125.156250 , -110.917969 ) , ylim = c( 32.287133 , 49.439557 ) )
plot( mf_circles , col = "azure2" , add = TRUE ) 
points( monkeyflower_train$lon , monkeyflower_train$lat , col = "red" )

```

*Note:* Gray region above is the study area for which background points were extracted.  The red points are the training points.


#### {-}



#### Bioclimatic covariates

A common procedure when building an SDM is to model the bioclimatic envelope, the geographic space that measures the relationship between species occurrences and regional climate (e.g. [Hutchinson 1957](doi:10.1101/SQB.1957.022.01.039) [Guisan & Zimmermann 2000](https://doi.org/10.1016/S0304-3800(00)00354-9) ; [Pearson et al. 2002](https://doi.org/10.1016/S0304-3800(02)00056-X) ; [Pearson & Dawson 2003]( https://doi.org/10.1046/j.1466-822X.2003.00042.x)). WorldClim ([Fick & Hijmans 2017](https://doi.org/10.1002/joc.5086)), a set of raster files with embedded climate data, is often used in building SDMs, particularly the 19 bioclimatic variables (BIO).  These variables are calculated by using monthly measured precipitation, maximum & minumum temperatures, and site altitude, over a 30 year window (1970-2000 for ver.2 ). 

We used the BIO variables for our static machine learning models. For our time series models, we used the raw monthly measurements for our time steps over the same time frame ( 360 time steps) These rasters can also be found on the WorldClim website (https://worldclim.org). 

#### Algorithms

There are 4 deep learning architectures provided by Keras that we used for our model building:

1. Convolutional neural networks (CNN)
2. Recurrent neural networks (RNNs)
3. Residual networks (ResNet)
4. Inception time networks 

All of these methods are extensions on the multi-layer perceptron, usually referred to as Artificial Neural Networks (ANN).  Traditionally, ANNs are feed-forward, have a fully connected network, and trained with back propagation and/or gradient descent learning algorithms. ANNs are especially helpful when computations are needed on large, complex data sets; however, this sort of power also leads to over-fitting. This is because the data are transformed using smoothing kernels at several steps within the learning procedure. The deep-learning architectures mentioned above were created to overcome this  by studying the raw data patterns directly.  Also, DLNNs are not entirely feed-forward; hat is, they tend to learn and self-correct at various steps in the internal processing instead after each learning iteration or epoch.   

For comparitive purposes, we used 3 popular and highly-productive machine learning algorithms for our static data analysis: Gradient Booosting Machines (GBM; e.g.,[Friedman 2001]( https://doi.org/10.1890/0012-9658(2007)88[243:BTFEMA]2.0.CO;2) [De'Ath 2007]( https://doi.org/10.1890/0012-9658(2007)88[243:BTFEMA]2.0.CO;2) ; [Elith et al. 2008](https://doi.org/10.1111/j.1365-2656.2008.01390.x) );  Maximum Entropy (MaxEnt; [Phillips et al. 2006](https://doi.org/10.1016/j.ecolmodel.2005.03.026) ; [Elith et al. 2011](https://doi.org/10.1111/j.1472-4642.2010.00725.x) ) ; and  Random Forest (RF;  [Brieman 2001](https://link.springer.com/article/10.1023/A:1010933404324) ; [Cutler et al. 2007](https://doi.org/10.1890/07-0539.1) ; [Evans et al. 2011](https://link.springer.com/chapter/10.1007/978-1-4419-7390-0_8) )



#### Modeling framework 

##### Time series deep learning 

For each species, we collected a bootstrap-sample of occurrences to match the number of background points, and  compiled our presence and background points into a a single, balanced data frame. We then extracted the values of each covariate at each time step for these points. Next we partitioned our data into several groups for the modeling procedure:

* train data set for candidate models (~35%; **At**) 
* validation data set for candidate models (~35%; **Av**) 
* At + Av, or train data set for selected model (~70%;  **Bt**) 
* validation data set for selecting # of epochs (~15%; **Bv**) 
* final reporting of classification performance (~15%; **T**) 

Once the data were partitioned the modeling procedure was as follows:

1. Create 5 randomly assembled models of each architecture (20 total candidate models).
    + Candidate models are built using **At** 
    + Evaluated using **Av** and classification accuracy
    + Run four epochs for each model  
    + Evaluated using classification accuracy 
2. Choose the best model, or the candidate with highest accuracy score.
3. Run 50 epochs 
    + In each epoch, the model is built using **Bt**
    + Evaluate model with **Bv**, calaculate accuracy and Area Under the receiver operating Curve (AUC)   
    + Each epoch updates internal parameters to improve model performance
4. Choose epoch model with best AUC as final model
5. Test model predictions using **T**
6. Calculate the AUC 


For the Monkeyflower models, we used a slightly different approach.  The testing set in the [Angert et al. (2018)](https://doi.org/10.1086/695984) study was used for **T**.  We then partitioned the sample from the training points to to match the 35:35:15:15 used in the other models.

##### Static machine learning 

Three static model sampling architectures were used for comparison:

1. Balanced-BIO 
    +  We used the same samples in **Bt** and **T** DLNNs to build and test our static models. The 19 BIO covariates were used in these models
2. Imbalanced-BIO
    + The common approach of taking the relatively small set of presence points and a significantly larger sample of background points and partitioning them into a train and test set.  Here we split both our occurrence  and background data 70:30 (train:test).  The 19 BIO covariates were used in these models
3. Balanced-WC
    + Similar to the Balanced-BIO, except we used the 4 WorldClim variables. We used altitude rsater and created three rasters for static covariates:  maximum measured temperature; minimum measured temperature; and averaged monthly precipitation.  

For all three architectures, AUC was calculated for model comparison. 

### Results {.tabset .tabset-pills}

#### 1000km {.tabset .tabset-pills}


```{r include=FALSE}

# Import training accuracies for comparison
training_acc_1000km <- read.csv("./Results_deep_learning/Accuracy_scores_1000km.csv")



# Import data for each species 

# AUCs 
auc_boar_1000km <- calc_epoch_aucs( 49 , path = "./Results_deep_learning/Boar/Boar_1000km/" )
auc_kudzu_1000km <- calc_epoch_aucs( 49 , path = "./Results_deep_learning/Kudzu/Kudzu_1000km/" )
auc_ladybird_1000km <- calc_epoch_aucs( 49 , path = "./Results_deep_learning/Ladybird/Ladybird_1000km/" )
auc_parakeet_1000km <- calc_epoch_aucs( 49 , path = "./Results_deep_learning/Parakeet/Parakeet_1000km/" )

n_epochs <- c(1:50)

# Max Points - Boar 
boar_max_train_1000km <- which( training_acc_1000km$Boar == max( training_acc_1000km$Boar) , arr.ind = TRUE )
boar_max_auc_1000km <- which( auc_boar_1000km == max( auc_boar_1000km ) , arr.ind = TRUE )

# Max Points - Kudzu
kudzu_max_train_1000km <- which( training_acc_1000km$Kudzu == max( training_acc_1000km$Kudzu ) , arr.ind = TRUE ) 
kudzu_max_auc_1000km <- which( auc_kudzu_1000km == max( auc_kudzu_1000km ) , arr.ind = TRUE )

# Max Points - Ladybird
ladybird_max_train_1000km <- which( training_acc_1000km$Ladybird  == max( training_acc_1000km$Ladybird ) , arr.ind = TRUE )
ladybird_max_auc_1000km <- which(auc_ladybird_1000km  == max(auc_ladybird_1000km ) , arr.ind = TRUE )

# Max Points - Parakeet 
parakeet_max_train_1000km <- which(training_acc_1000km$Parakeet == max(training_acc_1000km$Parakeet), arr.ind = TRUE )
parakeet_max_auc_1000km <- which( auc_parakeet_1000km == max( auc_parakeet_1000km ) , arr.ind = TRUE )

library(ggpubr)
```

##### DL Epoch Selection 
```{r echo=FALSE}

# Boar 
boar_data_1000km <- data.frame( n_epochs , training_acc_1000km$Boar , auc_boar_1000km )
colnames( boar_data_1000km ) <- c( "epoch" , "train accuracy" , " auc" )
boar_melt_1000km <- reshape2::melt( boar_data_1000km , id.var='epoch' ) 
boar_plot_1000km <- ggline(  data = boar_melt_1000km ,
                      x = "epoch" , 
                      y = "value" , 
                      color = "variable",
                      palette = c( "Forestgreen" ,# "Orange",
                                   "Blue" ) ,
                      fill = "variable",   
                      shape = 1 , 
                      #size = 2 ,
                      plot_type = "b" ) +
  annotate( "point" , x = boar_max_train_1000km , y = max(boar_data_1000km$`train accuracy` ) , colour = "Forestgreen" , size = 4 ) +
  annotate( "point" , x = boar_max_auc_1000km[1,1] , y = max( boar_data_1000km$` auc` ) , colour = "Blue" , size = 4 ) 




# Kudzu
kudzu_data_1000km <- data.frame( n_epochs , training_acc_1000km$Kudzu , auc_kudzu_1000km )
colnames(kudzu_data_1000km) <- c("epoch" , "train accuracy" , " auc" )
kudzu_melt_1000km <- reshape2::melt( kudzu_data_1000km , id.var='epoch' )
kudzu_plot_1000km <- ggline(  data = kudzu_melt_1000km ,
                       x = "epoch" ,
                       y = "value" ,
                       color = "variable",
                       palette = c( "Forestgreen" ,# "Orange", 
                                    "Blue" ) ,
                       fill = "variable",
                       shape = 1 ,
                       #size = 2 ,
                       plot_type = "b" ) +
  annotate("point", x = kudzu_max_train_1000km , y = max(kudzu_data_1000km$`train accuracy` ), colour = "Forestgreen" , size = 4 ) +
  annotate("point", x = kudzu_max_auc_1000km[,1] , y = max(kudzu_data_1000km$` auc`) , colour = "Blue" , size = 4 )

# Ladybird
ladybird_data_1000km <- data.frame( n_epochs , training_acc_1000km$Ladybird ,auc_ladybird_1000km )
colnames(ladybird_data_1000km) <- c("epoch" , "train accuracy" , " auc" )
ladybird_melt_1000km <- reshape2::melt( ladybird_data_1000km , id.var='epoch' )
ladybird_plot_1000km <- ggline(  data = ladybird_melt_1000km ,
                          x = "epoch" ,
                          y = "value" ,
                          color = "variable",
                          palette = c( "Forestgreen" , #"Orange", 
                                       "Blue" ) ,
                          fill = "variable",
                          shape = 1 ,
                          #size = 2 ,
                          plot_type = "b" ) +
  annotate("point", x = ladybird_max_train_1000km , y = max( ladybird_data_1000km$`train accuracy` ), colour = "Forestgreen" , size = 4 ) +
  annotate("point", x = ladybird_max_auc_1000km[,1] , y = max(ladybird_data_1000km$` auc`) , colour = "Blue" , size = 4 )

# Parakeet 
parakeet_data_1000km <- data.frame( n_epochs , training_acc_1000km$Parakeet ,  auc_parakeet_1000km )
colnames(parakeet_data_1000km) <- c("epoch" , "train accuracy" ,  " auc" )
parakeet_melt_1000km <- reshape2::melt( parakeet_data_1000km , id.var='epoch' ) 
parakeet_plot_1000km <- ggline(  data = parakeet_melt_1000km ,
                          x = "epoch" , 
                          y = "value" , 
                          color = "variable",
                          palette = c( "Forestgreen" , #"Orange",  
                                       "Blue" ) ,
                          fill = "variable",   
                          shape = 1 , 
                          #size = 2 ,
                          plot_type = "b" ) +
  annotate("point", x = parakeet_max_train_1000km, y = max(parakeet_data_1000km$`train accuracy` ), colour = "Forestgreen" , size = 4 ) +
  annotate("point", x = parakeet_max_auc_1000km[,1] , y = max( parakeet_data_1000km$` auc`) , colour = "Blue" , size = 4 )

# Combine all 
ggarrange( boar_plot_1000km +  rremove("xlab") +  rremove("x.text")  ,
           kudzu_plot_1000km +  rremove("xlab") +  rremove("x.text")  + rremove("y.axis") + rremove("ylab") +  rremove("y.text") + rremove( "y.ticks" ) ,
           ladybird_plot_1000km , 
           parakeet_plot_1000km + rremove("y.axis") +  rremove("ylab") +  rremove("y.text") + rremove( "y.ticks" ) ,
           ncol = 2 ,
           nrow = 2, 
           labels = "auto",
           common.legend = TRUE)

#print( "a.) Wild Boar, b.) Kudzu, c.) Ladybird d.) Monk Parakeet")

```
__a.)__ Wild Boar    __b.)__ Kudzu     __c.)__ Ladybird     __d.)__ Monk Parakeet


##### Model comparison {.tabset .tabset-pills}
```{r include=FALSE}

# worldclim
Static_model_worldclim_balanced_results_Boar_1000km <- readRDS("./Results_static_models/Static_model_worldclim_balanced_results_Boar_1000km.rds")
Static_model_worldclim_balanced_results_Kudzu_1000km <- readRDS("./Results_static_models/Static_model_worldclim_balanced_results_Kudzu_1000km.rds")
Static_model_worldclim_balanced_results_Ladybird_1000km <- readRDS("./Results_static_models/Static_model_worldclim_balanced_results_Ladybird_1000km.rds")
Static_model_worldclim_balanced_results_Parakeet_1000km <- readRDS("./Results_static_models/Static_model_worldclim_balanced_results_Parakeet_1000km.rds")


# bioclim -balanced
Static_model_bioclim_balanced_results_Boar_1000km <- readRDS("./Results_static_models/Static_model_bioclim_balanced_results_Boar_1000km.rds")
Static_model_bioclim_balanced_results_Kudzu_1000km <- readRDS("./Results_static_models/Static_model_bioclim_balanced_results_Kudzu_1000km.rds")
Static_model_bioclim_balanced_results_Ladybird_1000km <- readRDS("./Results_static_models/Static_model_bioclim_balanced_results_Ladybird_1000km.rds")
Static_model_bioclim_balanced_results_Parakeet_1000km <- readRDS("./Results_static_models/Static_model_bioclim_balanced_results_Parakeet_1000km.rds")


# bioclim -imimbalanced
Static_model_bioclim_imbalanced_results_Boar_1000km <- readRDS("./Results_static_models/Static_model_bioclim_imbalanced_results_Boar_1000km.rds")
Static_model_bioclim_imbalanced_results_Kudzu_1000km <- readRDS("./Results_static_models/Static_model_bioclim_imbalanced_results_Kudzu_1000km.rds")
Static_model_bioclim_imbalanced_results_Ladybird_1000km <- readRDS("./Results_static_models/Static_model_bioclim_imbalanced_results_Ladybird_1000km.rds")
Static_model_bioclim_imbalanced_results_Parakeet_1000km <- readRDS("./Results_static_models/Static_model_bioclim_imbalanced_results_Parakeet_1000km.rds")


library("pROC")
library("readr")
final_auc_Boar_1000km <- roc( data.frame( read_csv( "./Results_deep_learning/Best_models/Time_series_best_model_true_values_Boar_1000km.csv" ,  col_names = FALSE ) )$X1 , 
                       data.frame( read_csv( "./Results_deep_learning/Best_models/Time_series_best_model_test_predictions_Boar_1000km.csv" ,  col_names = FALSE ) )$X1 )$auc

final_auc_Kudzu_1000km <- roc( data.frame( read_csv( "./Results_deep_learning/Best_models/Time_series_best_model_true_values_Kudzu_1000km.csv" ,  col_names = FALSE ) )$X1 , 
                        data.frame( read_csv( "./Results_deep_learning/Best_models/Time_series_best_model_test_predictions_Kudzu_1000km.csv" ,  col_names = FALSE ) )$X1 )$auc

final_auc_Ladybird_1000km <- roc( data.frame( read_csv( "./Results_deep_learning/Best_models/Time_series_best_model_true_values_Ladybird_1000km.csv" ,  col_names = FALSE ) )$X1 , 
                           data.frame( read_csv( "./Results_deep_learning/Best_models/Time_series_best_model_test_predictions_Ladybird_1000km.csv" ,  col_names = FALSE ) )$X1 )$auc

final_auc_Parakeet_1000km <-   roc( data.frame( read_csv( "./Results_deep_learning/Best_models/Time_series_best_model_true_values_Parakeet_1000km.csv" ,  col_names = FALSE ) )$X1 ,
                             data.frame( read_csv( "./Results_deep_learning/Best_models/Time_series_best_model_test_predictions_Parakeet_1000km.csv" ,  col_names = FALSE ) )$X1 )$auc

types <- c("DLNN" , "GBM" , "MaxEnt" , "RF")

col = c(  "white", "darkorange", "white",
          "forestgreen", "goldenrod2" , "cornflowerblue",
          "forestgreen", "goldenrod2" , "cornflowerblue",
          "forestgreen", "goldenrod2" , "cornflowerblue" )

```

###### Boar

```{r echo=FALSE}

DL <-  c( 0 , final_auc_Boar_1000km , 0 )
WC_bal <- c( Static_model_worldclim_balanced_results_Boar_1000km[ , 1 ] )
Bio_bal <- c( Static_model_bioclim_balanced_results_Boar_1000km[ , 1 ] )
Bio_imbal <- c( Static_model_bioclim_imbalanced_results_Boar_1000km[ , 1 ] )
M_1000km <- as.matrix( data.frame( DL , WC_bal , Bio_bal , Bio_imbal ) )

par( mar = c( 5 , 4 , 4 , 5 ), xpd = TRUE )
barplot( M_1000km  ,  beside = TRUE , col = col , ylim = c( 0 , 1 ) )
legend( "right" , inset = c( - 0.1 , 0 ) , types , cex=0.6 , title = "Algorithm" ,
       fill=c( "darkorange" , "forestgreen" , "goldenrod2" , "cornflowerblue" ) )
title( "Model Predictions - Wild Boar" , line = + 3 )

# Insert values manually

text(2.5 , M_1000km[ 2 , 1 ] + 0.05 , round( M_1000km[ 2 , 1 ]  , 3 ), srt = 90 , cex = 0.8 )

text(5.5 , M_1000km[ 1 , 2 ] + 0.05 , round( M_1000km[ 1 , 2 ]  , 3 ), srt = 90 , cex = 0.8 )
text(6.5 , M_1000km[ 2 , 2 ] + 0.05 , round( M_1000km[ 2 , 2 ]  , 3 ), srt = 90 , cex = 0.8 )
text(7.5 , M_1000km[ 3 , 2 ] + 0.05 , round( M_1000km[ 3 , 2 ]  , 3 ), srt = 90 , cex = 0.8 )

text(9.5 , M_1000km[ 1 , 3 ] + 0.05 , round( M_1000km[ 1 , 3 ]  , 3 ), srt = 90 , cex = 0.8 )
text(10.5 , M_1000km[ 2 , 3 ] + 0.05 , round( M_1000km[ 2 , 3 ]  , 3 ), srt = 90 , cex = 0.8 )
text(11.5 , M_1000km[ 3 , 3 ] + 0.05 , round( M_1000km[ 3 , 3 ]  , 3 ), srt = 90 , cex = 0.8 )

text(13.5 , M_1000km[ 1 , 4 ] + 0.05 , round( M_1000km[ 1 , 4 ]  , 3 ), srt = 90 , cex = 0.8 )
text(14.5 , M_1000km[ 2 , 4 ] + 0.05 , round( M_1000km[ 2 , 4 ]  , 3 ), srt = 90 , cex = 0.8 )
text(15.5 , M_1000km[ 3 , 4 ] + 0.05 , round( M_1000km[ 3 , 4 ]  , 3 ), srt = 90 , cex = 0.8 )


```


###### Kudzu

```{r echo=FALSE}

DL <-  c( 0 , final_auc_Kudzu_1000km , 0 )
WC_bal <- c( Static_model_worldclim_balanced_results_Kudzu_1000km[ , 1 ] )
Bio_bal <- c( Static_model_bioclim_balanced_results_Kudzu_1000km[ , 1 ] )
Bio_imbal <- c( Static_model_bioclim_imbalanced_results_Kudzu_1000km[ , 1 ] )
M_1000km <- as.matrix( data.frame( DL , WC_bal , Bio_bal , Bio_imbal ) )

par( mar = c( 5 , 4 , 4 , 5 ), xpd = TRUE )
barplot( M_1000km  ,  beside = TRUE , col = col , ylim = c( 0 , 1 ) )
legend( "right" , inset = c( - 0.1 , 0 ) , types , cex=0.6 , title = "Algorithm" ,
       fill=c( "darkorange" , "forestgreen" , "goldenrod2" , "cornflowerblue" ) )
title( "Model Predictions - Kudzu" , line = + 3 )

# Insert values manually

text(2.5 , M_1000km[ 2 , 1 ] + 0.05 , round( M_1000km[ 2 , 1 ]  , 3 ), srt = 90 , cex = 0.8 )

text(5.5 , M_1000km[ 1 , 2 ] + 0.05 , round( M_1000km[ 1 , 2 ]  , 3 ), srt = 90 , cex = 0.8 )
text(6.5 , M_1000km[ 2 , 2 ] + 0.05 , round( M_1000km[ 2 , 2 ]  , 3 ), srt = 90 , cex = 0.8 )
text(7.5 , M_1000km[ 3 , 2 ] + 0.05 , round( M_1000km[ 3 , 2 ]  , 3 ), srt = 90 , cex = 0.8 )

text(9.5 , M_1000km[ 1 , 3 ] + 0.05 , round( M_1000km[ 1 , 3 ]  , 3 ), srt = 90 , cex = 0.8 )
text(10.5 , M_1000km[ 2 , 3 ] + 0.05 , round( M_1000km[ 2 , 3 ]  , 3 ), srt = 90 , cex = 0.8 )
text(11.5 , M_1000km[ 3 , 3 ] + 0.05 , round( M_1000km[ 3 , 3 ]  , 3 ), srt = 90 , cex = 0.8 )

text(13.5 , M_1000km[ 1 , 4 ] + 0.05 , round( M_1000km[ 1 , 4 ]  , 3 ), srt = 90 , cex = 0.8 )
text(14.5 , M_1000km[ 2 , 4 ] + 0.05 , round( M_1000km[ 2 , 4 ]  , 3 ), srt = 90 , cex = 0.8 )
text(15.5 , M_1000km[ 3 , 4 ] + 0.05 , round( M_1000km[ 3 , 4 ]  , 3 ), srt = 90 , cex = 0.8 )



```

###### Ladybird

```{r echo=FALSE}

DL <-  c( 0 , final_auc_Ladybird_1000km , 0 )
WC_bal <- c( Static_model_worldclim_balanced_results_Ladybird_1000km[ , 1 ] )
Bio_bal <- c( Static_model_bioclim_balanced_results_Ladybird_1000km[ , 1 ] )
Bio_imbal <- c( Static_model_bioclim_imbalanced_results_Ladybird_1000km[ , 1 ] )
M_1000km <- as.matrix( data.frame( DL , WC_bal , Bio_bal , Bio_imbal ) )

par( mar = c( 5 , 4 , 4 , 5 ), xpd = TRUE )
barplot( M_1000km  ,  beside = TRUE , col = col , ylim = c( 0 , 1 ) )
legend( "right" , inset = c( - 0.1 , 0 ) , types , cex=0.6 , title = "Algorithm" ,
       fill=c( "darkorange" , "forestgreen" , "goldenrod2" , "cornflowerblue" ) )
title( "Model Predictions - Ladybird" , line = + 3 )

# Insert values manually

text(2.5 , M_1000km[ 2 , 1 ] + 0.05 , round( M_1000km[ 2 , 1 ]  , 3 ), srt = 90 , cex = 0.8 )

text(5.5 , M_1000km[ 1 , 2 ] + 0.05 , round( M_1000km[ 1 , 2 ]  , 3 ), srt = 90 , cex = 0.8 )
text(6.5 , M_1000km[ 2 , 2 ] + 0.05 , round( M_1000km[ 2 , 2 ]  , 3 ), srt = 90 , cex = 0.8 )
text(7.5 , M_1000km[ 3 , 2 ] + 0.05 , round( M_1000km[ 3 , 2 ]  , 3 ), srt = 90 , cex = 0.8 )

text(9.5 , M_1000km[ 1 , 3 ] + 0.05 , round( M_1000km[ 1 , 3 ]  , 3 ), srt = 90 , cex = 0.8 )
text(10.5 , M_1000km[ 2 , 3 ] + 0.05 , round( M_1000km[ 2 , 3 ]  , 3 ), srt = 90 , cex = 0.8 )
text(11.5 , M_1000km[ 3 , 3 ] + 0.05 , round( M_1000km[ 3 , 3 ]  , 3 ), srt = 90 , cex = 0.8 )

text(13.5 , M_1000km[ 1 , 4 ] + 0.05 , round( M_1000km[ 1 , 4 ]  , 3 ), srt = 90 , cex = 0.8 )
text(14.5 , M_1000km[ 2 , 4 ] + 0.05 , round( M_1000km[ 2 , 4 ]  , 3 ), srt = 90 , cex = 0.8 )
text(15.5 , M_1000km[ 3 , 4 ] + 0.05 , round( M_1000km[ 3 , 4 ]  , 3 ), srt = 90 , cex = 0.8 )


```

###### Parakeet

```{r echo=FALSE}

DL <-  c( 0 , final_auc_Parakeet_1000km , 0 )
WC_bal <- c( Static_model_worldclim_balanced_results_Parakeet_1000km[ , 1 ] )
Bio_bal <- c( Static_model_bioclim_balanced_results_Parakeet_1000km[ , 1 ] )
Bio_imbal <- c( Static_model_bioclim_imbalanced_results_Parakeet_1000km[ , 1 ] )
M_1000km <- as.matrix( data.frame( DL , WC_bal , Bio_bal , Bio_imbal ) )

par( mar = c( 5 , 4 , 4 , 5 ), xpd = TRUE )
barplot( M_1000km  ,  beside = TRUE , col = col , ylim = c( 0 , 1 ) )
legend( "right" , inset = c( - 0.1 , 0 ) , types , cex=0.6 , title = "Algorithm" ,
       fill=c( "darkorange" , "forestgreen" , "goldenrod2" , "cornflowerblue" ) )
title( "Model Predictions - Parakeet" , line = + 3 )

# Insert values manually

text(2.5 , M_1000km[ 2 , 1 ] + 0.05 , round( M_1000km[ 2 , 1 ]  , 3 ), srt = 90 , cex = 0.8 )

text(5.5 , M_1000km[ 1 , 2 ] + 0.05 , round( M_1000km[ 1 , 2 ]  , 3 ), srt = 90 , cex = 0.8 )
text(6.5 , M_1000km[ 2 , 2 ] + 0.05 , round( M_1000km[ 2 , 2 ]  , 3 ), srt = 90 , cex = 0.8 )
text(7.5 , M_1000km[ 3 , 2 ] + 0.05 , round( M_1000km[ 3 , 2 ]  , 3 ), srt = 90 , cex = 0.8 )

text(9.5 , M_1000km[ 1 , 3 ] + 0.05 , round( M_1000km[ 1 , 3 ]  , 3 ), srt = 90 , cex = 0.8 )
text(10.5 , M_1000km[ 2 , 3 ] + 0.05 , round( M_1000km[ 2 , 3 ]  , 3 ), srt = 90 , cex = 0.8 )
text(11.5 , M_1000km[ 3 , 3 ] + 0.05 , round( M_1000km[ 3 , 3 ]  , 3 ), srt = 90 , cex = 0.8 )

text(13.5 , M_1000km[ 1 , 4 ] + 0.05 , round( M_1000km[ 1 , 4 ]  , 3 ), srt = 90 , cex = 0.8 )
text(14.5 , M_1000km[ 2 , 4 ] + 0.05 , round( M_1000km[ 2 , 4 ]  , 3 ), srt = 90 , cex = 0.8 )
text(15.5 , M_1000km[ 3 , 4 ] + 0.05 , round( M_1000km[ 3 , 4 ]  , 3 ), srt = 90 , cex = 0.8 )

```

##### {-}

#### Global {.tabset .tabset-pills}


```{r include=FALSE}

# Import training accuracies for comparison
training_acc_global <- read.csv("./Results_deep_learning/Accuracy_scores_global.csv")



# Import data for each species 

# AUCs 
auc_boar_global <- calc_epoch_aucs( 49 , path = "./Results_deep_learning/Boar/Boar_global/" )
auc_kudzu_global <- calc_epoch_aucs( 49 , path = "./Results_deep_learning/Kudzu/Kudzu_global/" )
auc_ladybird_global <- calc_epoch_aucs( 49 , path = "./Results_deep_learning/Ladybird/Ladybird_global/" )
auc_parakeet_global <- calc_epoch_aucs( 49 , path = "./Results_deep_learning/Parakeet/Parakeet_global/" )

n_epochs <- c(1:50)

# Max Points - Boar 
boar_max_train_global <- which( training_acc_global$Boar == max( training_acc_global$Boar) , arr.ind = TRUE )
boar_max_auc_global <- which( auc_boar_global == max( auc_boar_global ) , arr.ind = TRUE )

# Max Points - Kudzu
kudzu_max_train_global <- which( training_acc_global$Kudzu == max( training_acc_global$Kudzu ) , arr.ind = TRUE ) 
kudzu_max_auc_global <- which( auc_kudzu_global == max( auc_kudzu_global ) , arr.ind = TRUE )

# Max Points - Ladybird
ladybird_max_train_global <- which( training_acc_global$Ladybird  == max( training_acc_global$Ladybird ) , arr.ind = TRUE )
ladybird_max_auc_global <- which(auc_ladybird_global  == max(auc_ladybird_global ) , arr.ind = TRUE )

# Max Points - Parakeet 
parakeet_max_train_global <- which(training_acc_global$Parakeet == max(training_acc_global$Parakeet), arr.ind = TRUE )
parakeet_max_auc_global <- which( auc_parakeet_global == max( auc_parakeet_global ) , arr.ind = TRUE )

library(ggpubr)
```

##### DL Epoch Selection 
```{r echo=FALSE}

# Boar 
boar_data_global <- data.frame( n_epochs , training_acc_global$Boar , auc_boar_global )
colnames( boar_data_global ) <- c( "epoch" , "train accuracy" , " auc" )
boar_melt_global <- reshape2::melt( boar_data_global , id.var='epoch' ) 
boar_plot_global <- ggline(  data = boar_melt_global ,
                             
                             x = "epoch" , 
                             y = "value" , 
                             color = "variable",
                             palette = c( "Forestgreen" , "Blue" ) ,
                             fill = "variable",   
                            shape = 1 , 
                           #ylim = c( 80 , 100 ) ,
                      #size = 2 ,
                      plot_type = "b" ) +
  annotate( "point" , x = boar_max_train_global , y = max(boar_data_global$`train accuracy` ) , colour = "Forestgreen" , size = 4 ) +
  annotate( "point" , x = boar_max_auc_global[1,1] , y = max( boar_data_global$` auc` ) , colour = "Blue" , size = 4 ) 




# Kudzu
kudzu_data_global <- data.frame( n_epochs , training_acc_global$Kudzu , auc_kudzu_global )
colnames(kudzu_data_global) <- c("epoch" , "train accuracy" , " auc" )
kudzu_melt_global <- reshape2::melt( kudzu_data_global , id.var='epoch' )
kudzu_plot_global <- ggline(  data = kudzu_melt_global ,
                       x = "epoch" ,
                       y = "value" ,
                       color = "variable",
                       palette = c( "Forestgreen" ,# "Orange", 
                                    "Blue" ) ,
                       fill = "variable",
                       shape = 1 ,
                       
                       #size = 2 ,
                       plot_type = "b" ) +
  annotate("point", x = kudzu_max_train_global , y = max(kudzu_data_global$`train accuracy` ), colour = "Forestgreen" , size = 4 ) +
  annotate("point", x = kudzu_max_auc_global[,1] , y = max(kudzu_data_global$` auc`) , colour = "Blue" , size = 4 )

# Ladybird
ladybird_data_global <- data.frame( n_epochs , training_acc_global$Ladybird ,auc_ladybird_global )
colnames(ladybird_data_global) <- c("epoch" , "train accuracy" , " auc" )
ladybird_melt_global <- reshape2::melt( ladybird_data_global , id.var='epoch' )
ladybird_plot_global <- ggline(  data = ladybird_melt_global ,
                          x = "epoch" ,
                          y = "value" ,
                          color = "variable",
                          palette = c( "Forestgreen" , #"Orange", 
                                       "Blue" ) ,
                          fill = "variable",
                          shape = 1 ,
                          
                          #size = 2 ,
                          plot_type = "b" ) +
  annotate("point", x = ladybird_max_train_global , y = max( ladybird_data_global$`train accuracy` ), colour = "Forestgreen" , size = 4 ) +
  annotate("point", x = ladybird_max_auc_global[,1] , y = max(ladybird_data_global$` auc`) , colour = "Blue" , size = 4 )

# Parakeet 
parakeet_data_global <- data.frame( n_epochs , training_acc_global$Parakeet ,  auc_parakeet_global )
colnames(parakeet_data_global) <- c("epoch" , "train accuracy" ,  " auc" )
parakeet_melt_global <- reshape2::melt( parakeet_data_global , id.var='epoch' ) 
parakeet_plot_global <- ggline(  data = parakeet_melt_global ,
                          x = "epoch" , 
                          y = "value" , 
                          color = "variable",
                          palette = c( "Forestgreen" , #"Orange",  
                                       "Blue" ) ,
                          fill = "variable",   
                          shape = 1 , 
                         
                          #size = 2 ,
                          plot_type = "b" ) +
  annotate("point", x = parakeet_max_train_global, y = max(parakeet_data_global$`train accuracy` ), colour = "Forestgreen" , size = 4 ) +
  annotate("point", x = parakeet_max_auc_global[,1] , y = max( parakeet_data_global$` auc`) , colour = "Blue" , size = 4 )

# Combine all 
ggarrange( boar_plot_global +  rremove("xlab") +  rremove("x.text")  ,
           kudzu_plot_global +  rremove("xlab") +  rremove("x.text")  + rremove("y.axis") + rremove("ylab") +  rremove("y.text") + rremove( "y.ticks" ) ,
           ladybird_plot_global , 
           parakeet_plot_global + rremove("y.axis") +  rremove("ylab") +  rremove("y.text") + rremove( "y.ticks" ) ,
           ncol = 2 ,
           nrow = 2, 
           labels = "auto",
           common.legend = TRUE)

#print( "a.) Wild Boar, b.) Kudzu, c.) Ladybird d.) Monk Parakeet")

```
__a.)__ Wild Boar    __b.)__ Kudzu     __c.)__ Ladybird     __d.)__ Monk Parakeet


##### Model comparison {.tabset .tabset-pills}
```{r include=FALSE}

# worldclim
Static_model_worldclim_balanced_results_Boar_global <- readRDS("./Results_static_models/Static_model_worldclim_balanced_results_Boar_global.rds")
Static_model_worldclim_balanced_results_Kudzu_global <- readRDS("./Results_static_models/Static_model_worldclim_balanced_results_Kudzu_global.rds")
Static_model_worldclim_balanced_results_Ladybird_global <- readRDS("./Results_static_models/Static_model_worldclim_balanced_results_Ladybird_global.rds")
Static_model_worldclim_balanced_results_Parakeet_global <- readRDS("./Results_static_models/Static_model_worldclim_balanced_results_Parakeet_global.rds")


# bioclim -balanced
Static_model_bioclim_balanced_results_Boar_global <- readRDS("./Results_static_models/Static_model_bioclim_balanced_results_Boar_global.rds")
Static_model_bioclim_balanced_results_Kudzu_global <- readRDS("./Results_static_models/Static_model_bioclim_balanced_results_Kudzu_global.rds")
Static_model_bioclim_balanced_results_Ladybird_global <- readRDS("./Results_static_models/Static_model_bioclim_balanced_results_Ladybird_global.rds")
Static_model_bioclim_balanced_results_Parakeet_global <- readRDS("./Results_static_models/Static_model_bioclim_balanced_results_Parakeet_global.rds")


# bioclim -imimbalanced
Static_model_bioclim_imbalanced_results_Boar_global <- readRDS("./Results_static_models/Static_model_bioclim_imbalanced_results_Boar_global.rds")
Static_model_bioclim_imbalanced_results_Kudzu_global <- readRDS("./Results_static_models/Static_model_bioclim_imbalanced_results_Kudzu_global.rds")
Static_model_bioclim_imbalanced_results_Ladybird_global <- readRDS("./Results_static_models/Static_model_bioclim_imbalanced_results_Ladybird_global.rds")
Static_model_bioclim_imbalanced_results_Parakeet_global <- readRDS("./Results_static_models/Static_model_bioclim_imbalanced_results_Parakeet_global.rds")


library("pROC")
library("readr")
final_auc_Boar_global <- roc( data.frame( read_csv( "./Results_deep_learning/Best_models/Time_series_best_model_true_values_Boar_global.csv" ,  col_names = FALSE ) )$X1 , 
                       data.frame( read_csv( "./Results_deep_learning/Best_models/Time_series_best_model_test_predictions_Boar_global.csv" ,  col_names = FALSE ) )$X1 )$auc

final_auc_Kudzu_global <- roc( data.frame( read_csv( "./Results_deep_learning/Best_models/Time_series_best_model_true_values_Kudzu_global.csv" ,  col_names = FALSE ) )$X1 , 
                        data.frame( read_csv( "./Results_deep_learning/Best_models/Time_series_best_model_test_predictions_Kudzu_global.csv" ,  col_names = FALSE ) )$X1 )$auc

final_auc_Ladybird_global <- roc( data.frame( read_csv( "./Results_deep_learning/Best_models/Time_series_best_model_true_values_Ladybird_global.csv" ,  col_names = FALSE ) )$X1 , 
                           data.frame( read_csv( "./Results_deep_learning/Best_models/Time_series_best_model_test_predictions_Ladybird_global.csv" ,  col_names = FALSE ) )$X1 )$auc

final_auc_Parakeet_global <-   roc( data.frame( read_csv( "./Results_deep_learning/Best_models/Time_series_best_model_true_values_Parakeet_global.csv" ,  col_names = FALSE ) )$X1 ,
                             data.frame( read_csv( "./Results_deep_learning/Best_models/Time_series_best_model_test_predictions_Parakeet_global.csv" ,  col_names = FALSE ) )$X1 )$auc

types <- c("DLNN" , "GBM" , "MaxEnt" , "RF")

col = c(  "white", "darkorange", "white",
          "forestgreen", "goldenrod2" , "cornflowerblue",
          "forestgreen", "goldenrod2" , "cornflowerblue",
          "forestgreen", "goldenrod2" , "cornflowerblue" )

```

###### Boar

```{r echo=FALSE}

DL <-  c( 0 , final_auc_Boar_global , 0 )
WC_bal <- c( Static_model_worldclim_balanced_results_Boar_global[ , 1 ] )
Bio_bal <- c( Static_model_bioclim_balanced_results_Boar_global[ , 1 ] )
Bio_imbal <- c( Static_model_bioclim_imbalanced_results_Boar_global[ , 1 ] )
M_global <- as.matrix( data.frame( DL , WC_bal , Bio_bal , Bio_imbal ) )

par( mar = c( 5 , 4 , 4 , 5 ), xpd = TRUE )
barplot( M_global  ,  beside = TRUE , col = col , ylim = c( 0 , 1 ) )
legend( "right" , inset = c( - 0.1 , 0 ) , types , cex=0.6 , title = "Algorithm" ,
       fill=c( "darkorange" , "forestgreen" , "goldenrod2" , "cornflowerblue" ) )
title( "Model Predictions - Wild Boar" , line = + 3 )

# Insert values manually

text(2.5 , M_global[ 2 , 1 ] + 0.05 , round( M_global[ 2 , 1 ]  , 3 ), srt = 90 , cex = 0.8 )

text(5.5 , M_global[ 1 , 2 ] + 0.05 , round( M_global[ 1 , 2 ]  , 3 ), srt = 90 , cex = 0.8 )
text(6.5 , M_global[ 2 , 2 ] + 0.05 , round( M_global[ 2 , 2 ]  , 3 ), srt = 90 , cex = 0.8 )
text(7.5 , M_global[ 3 , 2 ] + 0.05 , round( M_global[ 3 , 2 ]  , 3 ), srt = 90 , cex = 0.8 )

text(9.5 , M_global[ 1 , 3 ] + 0.05 , round( M_global[ 1 , 3 ]  , 3 ), srt = 90 , cex = 0.8 )
text(10.5 , M_global[ 2 , 3 ] + 0.05 , round( M_global[ 2 , 3 ]  , 3 ), srt = 90 , cex = 0.8 )
text(11.5 , M_global[ 3 , 3 ] + 0.05 , round( M_global[ 3 , 3 ]  , 3 ), srt = 90 , cex = 0.8 )

text(13.5 , M_global[ 1 , 4 ] + 0.05 , round( M_global[ 1 , 4 ]  , 3 ), srt = 90 , cex = 0.8 )
text(14.5 , M_global[ 2 , 4 ] + 0.05 , round( M_global[ 2 , 4 ]  , 3 ), srt = 90 , cex = 0.8 )
text(15.5 , M_global[ 3 , 4 ] + 0.05 , round( M_global[ 3 , 4 ]  , 3 ), srt = 90 , cex = 0.8 )


```


###### Kudzu

```{r echo=FALSE}

DL <-  c( 0 , final_auc_Kudzu_global , 0 )
WC_bal <- c( Static_model_worldclim_balanced_results_Kudzu_global[ , 1 ] )
Bio_bal <- c( Static_model_bioclim_balanced_results_Kudzu_global[ , 1 ] )
Bio_imbal <- c( Static_model_bioclim_imbalanced_results_Kudzu_global[ , 1 ] )
M_global <- as.matrix( data.frame( DL , WC_bal , Bio_bal , Bio_imbal ) )

par( mar = c( 5 , 4 , 4 , 5 ), xpd = TRUE )
barplot( M_global  ,  beside = TRUE , col = col , ylim = c( 0 , 1 ) )
legend( "right" , inset = c( - 0.1 , 0 ) , types , cex=0.6 , title = "Algorithm" ,
       fill=c( "darkorange" , "forestgreen" , "goldenrod2" , "cornflowerblue" ) )
title( "Model Predictions - Kudzu" , line = + 3 )

# Insert values manually

text(2.5 , M_global[ 2 , 1 ] + 0.05 , round( M_global[ 2 , 1 ]  , 3 ), srt = 90 , cex = 0.8 )

text(5.5 , M_global[ 1 , 2 ] + 0.05 , round( M_global[ 1 , 2 ]  , 3 ), srt = 90 , cex = 0.8 )
text(6.5 , M_global[ 2 , 2 ] + 0.05 , round( M_global[ 2 , 2 ]  , 3 ), srt = 90 , cex = 0.8 )
text(7.5 , M_global[ 3 , 2 ] + 0.05 , round( M_global[ 3 , 2 ]  , 3 ), srt = 90 , cex = 0.8 )

text(9.5 , M_global[ 1 , 3 ] + 0.05 , round( M_global[ 1 , 3 ]  , 3 ), srt = 90 , cex = 0.8 )
text(10.5 , M_global[ 2 , 3 ] + 0.05 , round( M_global[ 2 , 3 ]  , 3 ), srt = 90 , cex = 0.8 )
text(11.5 , M_global[ 3 , 3 ] + 0.05 , round( M_global[ 3 , 3 ]  , 3 ), srt = 90 , cex = 0.8 )

text(13.5 , M_global[ 1 , 4 ] + 0.05 , round( M_global[ 1 , 4 ]  , 3 ), srt = 90 , cex = 0.8 )
text(14.5 , M_global[ 2 , 4 ] + 0.05 , round( M_global[ 2 , 4 ]  , 3 ), srt = 90 , cex = 0.8 )
text(15.5 , M_global[ 3 , 4 ] + 0.05 , round( M_global[ 3 , 4 ]  , 3 ), srt = 90 , cex = 0.8 )



```

###### Ladybird

```{r echo=FALSE}

DL <-  c( 0 , final_auc_Ladybird_global , 0 )
WC_bal <- c( Static_model_worldclim_balanced_results_Ladybird_global[ , 1 ] )
Bio_bal <- c( Static_model_bioclim_balanced_results_Ladybird_global[ , 1 ] )
Bio_imbal <- c( Static_model_bioclim_imbalanced_results_Ladybird_global[ , 1 ] )
M_global <- as.matrix( data.frame( DL , WC_bal , Bio_bal , Bio_imbal ) )

par( mar = c( 5 , 4 , 4 , 5 ), xpd = TRUE )
barplot( M_global  ,  beside = TRUE , col = col , ylim = c( 0 , 1 ) )
legend( "right" , inset = c( - 0.1 , 0 ) , types , cex=0.6 , title = "Algorithm" ,
       fill=c( "darkorange" , "forestgreen" , "goldenrod2" , "cornflowerblue" ) )
title( "Model Predictions - Ladybird" , line = + 3 )

# Insert values manually

text(2.5 , M_global[ 2 , 1 ] + 0.05 , round( M_global[ 2 , 1 ]  , 3 ), srt = 90 , cex = 0.8 )

text(5.5 , M_global[ 1 , 2 ] + 0.05 , round( M_global[ 1 , 2 ]  , 3 ), srt = 90 , cex = 0.8 )
text(6.5 , M_global[ 2 , 2 ] + 0.05 , round( M_global[ 2 , 2 ]  , 3 ), srt = 90 , cex = 0.8 )
text(7.5 , M_global[ 3 , 2 ] + 0.05 , round( M_global[ 3 , 2 ]  , 3 ), srt = 90 , cex = 0.8 )

text(9.5 , M_global[ 1 , 3 ] + 0.05 , round( M_global[ 1 , 3 ]  , 3 ), srt = 90 , cex = 0.8 )
text(10.5 , M_global[ 2 , 3 ] + 0.05 , round( M_global[ 2 , 3 ]  , 3 ), srt = 90 , cex = 0.8 )
text(11.5 , M_global[ 3 , 3 ] + 0.05 , round( M_global[ 3 , 3 ]  , 3 ), srt = 90 , cex = 0.8 )

text(13.5 , M_global[ 1 , 4 ] + 0.05 , round( M_global[ 1 , 4 ]  , 3 ), srt = 90 , cex = 0.8 )
text(14.5 , M_global[ 2 , 4 ] + 0.05 , round( M_global[ 2 , 4 ]  , 3 ), srt = 90 , cex = 0.8 )
text(15.5 , M_global[ 3 , 4 ] + 0.05 , round( M_global[ 3 , 4 ]  , 3 ), srt = 90 , cex = 0.8 )


```

###### Parakeet

```{r echo=FALSE}

DL <-  c( 0 , final_auc_Parakeet_global , 0 )
WC_bal <- c( Static_model_worldclim_balanced_results_Parakeet_global[ , 1 ] )
Bio_bal <- c( Static_model_bioclim_balanced_results_Parakeet_global[ , 1 ] )
Bio_imbal <- c( Static_model_bioclim_imbalanced_results_Parakeet_global[ , 1 ] )
M_global <- as.matrix( data.frame( DL , WC_bal , Bio_bal , Bio_imbal ) )

par( mar = c( 5 , 4 , 4 , 5 ), xpd = TRUE )
barplot( M_global  ,  beside = TRUE , col = col , ylim = c( 0 , 1 ) )
legend( "right" , inset = c( - 0.1 , 0 ) , types , cex=0.6 , title = "Algorithm" ,
       fill=c( "darkorange" , "forestgreen" , "goldenrod2" , "cornflowerblue" ) )
title( "Model Predictions - Parakeet" , line = + 3 )

# Insert values manually

text(2.5 , M_global[ 2 , 1 ] + 0.05 , round( M_global[ 2 , 1 ]  , 3 ), srt = 90 , cex = 0.8 )

text(5.5 , M_global[ 1 , 2 ] + 0.05 , round( M_global[ 1 , 2 ]  , 3 ), srt = 90 , cex = 0.8 )
text(6.5 , M_global[ 2 , 2 ] + 0.05 , round( M_global[ 2 , 2 ]  , 3 ), srt = 90 , cex = 0.8 )
text(7.5 , M_global[ 3 , 2 ] + 0.05 , round( M_global[ 3 , 2 ]  , 3 ), srt = 90 , cex = 0.8 )

text(9.5 , M_global[ 1 , 3 ] + 0.05 , round( M_global[ 1 , 3 ]  , 3 ), srt = 90 , cex = 0.8 )
text(10.5 , M_global[ 2 , 3 ] + 0.05 , round( M_global[ 2 , 3 ]  , 3 ), srt = 90 , cex = 0.8 )
text(11.5 , M_global[ 3 , 3 ] + 0.05 , round( M_global[ 3 , 3 ]  , 3 ), srt = 90 , cex = 0.8 )

text(13.5 , M_global[ 1 , 4 ] + 0.05 , round( M_global[ 1 , 4 ]  , 3 ), srt = 90 , cex = 0.8 )
text(14.5 , M_global[ 2 , 4 ] + 0.05 , round( M_global[ 2 , 4 ]  , 3 ), srt = 90 , cex = 0.8 )
text(15.5 , M_global[ 3 , 4 ] + 0.05 , round( M_global[ 3 , 4 ]  , 3 ), srt = 90 , cex = 0.8 )

```

##### {-}

#### P/A {.tabset .tabset-pills}

```{r include=FALSE}

# Import training accuracies for comparison
training_acc_monkeyflower <- read.csv("./Results_deep_learning/Accuracy_scores_donut.csv")

n_epochs <- c(1:50)

# Import data for each species 

# AUCs 
auc_monkeyflower_donut <- calc_epoch_aucs( 49 , path = "./Results_deep_learning/Monkeyflower/Monkeyflower_donut/" )

final_auc_Monekyflower_donut <- roc( data.frame( read_csv( "./Results_deep_learning/Best_models/Time_series_best_model_true_values_Monkeyflower.csv" ,  col_names = FALSE ) )$X1 , 
                       data.frame( read_csv( "./Results_deep_learning/Best_models/Time_series_best_model_test_predictions_Monkeyflower.csv" ,  col_names = FALSE ) )$X1 )$auc

# Max Points - Monkeyflower
monkeyflower_max_train_global <- which( training_acc_monkeyflower$Monkeyflower == max( training_acc_monkeyflower$Monkeyflower ) , arr.ind = TRUE )
monkeyflower_max_auc_global <- which( auc_monkeyflower_donut  == max( auc_monkeyflower_donut  ) , arr.ind = TRUE )


Static_model_worldclim_balanced_results_Monkeyflower_donut <- readRDS("./Results_static_models/Static_model_worldclim_balanced_results_Monkeyflower_donut.rds")
Static_model_bioclim_balanced_results_Monkeyflower_donut <- readRDS("./Results_static_models/Static_model_bioclim_balanced_results_Monkeyflower_donut.rds")
Static_model_bioclim_imbalanced_results_Monkeyflower_donut <- readRDS("./Results_static_models/Static_model_bioclim_imbalanced_results_Monkeyflower_donut.rds")


```


##### DL Epoch Selection
```{r echo=FALSE}
monkeyflower_data_global <- data.frame( n_epochs , training_acc_monkeyflower$Monkeyflower  , auc_monkeyflower_donut )
colnames( monkeyflower_data_global ) <- c( "epoch" , "train accuracy" , " auc" )
monkeyflower_melt_global <- reshape2::melt( monkeyflower_data_global , id.var='epoch' ) 
monkeyflower_plot_global <- ggline(  data = monkeyflower_melt_global ,
                             
                             x = "epoch" , 
                             y = "value" , 
                             color = "variable",
                             palette = c( "Forestgreen" , "Blue" ) ,
                             fill = "variable",   
                            shape = 1 , 
                           #ylim = c( 80 , 100 ) ,
                      #size = 2 ,
                      plot_type = "b" ) +
  annotate( "point" , x = monkeyflower_max_train_global , y = max(monkeyflower_data_global$`train accuracy` ) , colour = "Forestgreen" , size = 4 ) +
  annotate( "point" , x = monkeyflower_max_auc_global[1,1] , y = max( monkeyflower_data_global$` auc` ) , colour = "Blue" , size = 4 ) 
monkeyflower_plot_global
```


##### DL Model Comparison
```{r echo=FALSE}

types <- c("DLNN" , "GBM" , "MaxEnt" , "RF")

col = c(  "white", "darkorange", "white",
          "forestgreen", "goldenrod2" , "cornflowerblue",
          "forestgreen", "goldenrod2" , "cornflowerblue",
          "forestgreen", "goldenrod2" , "cornflowerblue" )


DL <-  c( 0 , final_auc_Monekyflower_donut , 0 )
WC_bal <- c( Static_model_worldclim_balanced_results_Monkeyflower_donut[ , 1 ] )
Bio_bal <- c( Static_model_bioclim_balanced_results_Monkeyflower_donut[ , 1 ] )
Bio_imbal <- c( Static_model_bioclim_imbalanced_results_Monkeyflower_donut[ , 1 ] )
M_global <- as.matrix( data.frame( DL , WC_bal , Bio_bal , Bio_imbal ) )

par( mar = c( 5 , 4 , 4 , 5 ), xpd = TRUE )
barplot( M_global  ,  beside = TRUE , col = col , ylim = c( 0 , 1 ) )
legend( "right" , inset = c( - 0.1 , 0 ) , types , cex=0.6 , title = "Algorithm" ,
       fill=c( "darkorange" , "forestgreen" , "goldenrod2" , "cornflowerblue" ) )
title( "Model Predictions - Monkeyflower" , line = + 3 )

# Insert values manually

text(2.5 , M_global[ 2 , 1 ] + 0.05 , round( M_global[ 2 , 1 ]  , 3 ), srt = 90 , cex = 0.8 )

text(5.5 , M_global[ 1 , 2 ] + 0.05 , round( M_global[ 1 , 2 ]  , 3 ), srt = 90 , cex = 0.8 )
text(6.5 , M_global[ 2 , 2 ] + 0.05 , round( M_global[ 2 , 2 ]  , 3 ), srt = 90 , cex = 0.8 )
text(7.5 , M_global[ 3 , 2 ] + 0.05 , round( M_global[ 3 , 2 ]  , 3 ), srt = 90 , cex = 0.8 )

text(9.5 , M_global[ 1 , 3 ] + 0.05 , round( M_global[ 1 , 3 ]  , 3 ), srt = 90 , cex = 0.8 )
text(10.5 , M_global[ 2 , 3 ] + 0.05 , round( M_global[ 2 , 3 ]  , 3 ), srt = 90 , cex = 0.8 )
text(11.5 , M_global[ 3 , 3 ] + 0.05 , round( M_global[ 3 , 3 ]  , 3 ), srt = 90 , cex = 0.8 )

text(13.5 , M_global[ 1 , 4 ] + 0.05 , round( M_global[ 1 , 4 ]  , 3 ), srt = 90 , cex = 0.8 )
text(14.5 , M_global[ 2 , 4 ] + 0.05 , round( M_global[ 2 , 4 ]  , 3 ), srt = 90 , cex = 0.8 )
text(15.5 , M_global[ 3 , 4 ] + 0.05 , round( M_global[ 3 , 4 ]  , 3 ), srt = 90 , cex = 0.8 )

```




### {-}

### Predictions {.tabset .tabset-pills}
```{r echo=FALSE}

##############################
# DL Models
##############################

#./Results_all_predictiction_rasters/

# Boar
DL_Boar_1000km <- raster("./Results_all_predictiction_rasters/DL_Boar_1000km.tif")
DL_Boar_global <- raster("./Results_all_predictiction_rasters/DL_Boar_global.tif")

# Kudzu
DL_Kudzu_1000km <- raster("./Results_all_predictiction_rasters/DL_Kudzu_1000km.tif")
DL_Kudzu_global <- raster("./Results_all_predictiction_rasters/DL_Kudzu_global.tif")

# Ladybird
DL_Ladybird_1000km <- raster("./Results_all_predictiction_rasters/DL_Ladybird_1000km.tif")
DL_Ladybird_global <- raster("./Results_all_predictiction_rasters/DL_Ladybird_global.tif")

# Parakeet
DL_Parakeet_1000km <- raster("./Results_all_predictiction_rasters/DL_Parakeet_1000km.tif")
DL_Parakeet_global <- raster("./Results_all_predictiction_rasters/DL_Parakeet_global.tif")


##############################
# Static Models
##############################


# Boar -  bioclim balanced
Static_model_bioclim_balanced_Boar_gbm_1000km <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_balanced_Boar_gbm_1000km.tif")
Static_model_bioclim_balanced_Boar_maxent_1000km <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_balanced_Boar_maxent_1000km.tif")
Static_model_bioclim_balanced_Boar_rf_1000km <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_balanced_Boar_rf_1000km.tif")

Static_model_bioclim_balanced_Boar_gbm_global <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_balanced_Boar_gbm_global.tif")
Static_model_bioclim_balanced_Boar_maxent_global <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_balanced_Boar_maxent_global.tif")
Static_model_bioclim_balanced_Boar_rf_global <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_balanced_Boar_rf_global.tif")

# Boar -  bioclim imbalanced
Static_model_bioclim_imbalanced_Boar_gbm_1000km <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_imbalanced_Boar_gbm_1000km.tif")
Static_model_bioclim_imbalanced_Boar_maxent_1000km <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_imbalanced_Boar_maxent_1000km.tif")
Static_model_bioclim_imbalanced_Boar_rf_1000km <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_imbalanced_Boar_rf_1000km.tif")

Static_model_bioclim_imbalanced_Boar_gbm_global <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_imbalanced_Boar_gbm_global.tif")
Static_model_bioclim_imbalanced_Boar_maxent_global <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_imbalanced_Boar_maxent_global.tif")
Static_model_bioclim_imbalanced_Boar_rf_global <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_imbalanced_Boar_rf_global.tif")

# Boar -  worldclim balanced
Static_model_worldclim_balanced_Boar_gbm_1000km <- raster("./Results_all_predictiction_rasters/Static_model_worldclim_balanced_Boar_gbm_1000km.tif")
Static_model_worldclim_balanced_Boar_maxent_1000km <- raster("./Results_all_predictiction_rasters/Static_model_worldclim_balanced_Boar_maxent_1000km.tif")
Static_model_worldclim_balanced_Boar_rf_1000km <- raster("./Results_all_predictiction_rasters/Static_model_worldclim_balanced_Boar_rf_1000km.tif")

Static_model_worldclim_balanced_Boar_gbm_global <- raster("./Results_all_predictiction_rasters/Static_model_worldclim_balanced_Boar_gbm_global.tif")
Static_model_worldclim_balanced_Boar_maxent_global <- raster("./Results_all_predictiction_rasters/Static_model_worldclim_balanced_Boar_maxent_global.tif")
Static_model_worldclim_balanced_Boar_rf_global <- raster("./Results_all_predictiction_rasters/Static_model_worldclim_balanced_Boar_rf_global.tif")

#____________________________________________________________________________________________________________________________________

# Kudzu -  bioclim balanced
Static_model_bioclim_balanced_Kudzu_gbm_1000km <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_balanced_Kudzu_gbm_1000km.tif")
Static_model_bioclim_balanced_Kudzu_maxent_1000km <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_balanced_Kudzu_maxent_1000km.tif")
Static_model_bioclim_balanced_Kudzu_rf_1000km <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_balanced_Kudzu_rf_1000km.tif")

Static_model_bioclim_balanced_Kudzu_gbm_global <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_balanced_Kudzu_gbm_global.tif")
Static_model_bioclim_balanced_Kudzu_maxent_global <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_balanced_Kudzu_maxent_global.tif")
Static_model_bioclim_balanced_Kudzu_rf_global <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_balanced_Kudzu_rf_global.tif")

# Kudzu -  bioclim imbalanced
Static_model_bioclim_imbalanced_Kudzu_gbm_1000km <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_imbalanced_Kudzu_gbm_1000km.tif")
Static_model_bioclim_imbalanced_Kudzu_maxent_1000km <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_imbalanced_Kudzu_maxent_1000km.tif")
Static_model_bioclim_imbalanced_Kudzu_rf_1000km <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_imbalanced_Kudzu_rf_1000km.tif")

Static_model_bioclim_imbalanced_Kudzu_gbm_global <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_imbalanced_Kudzu_gbm_global.tif")
Static_model_bioclim_imbalanced_Kudzu_maxent_global <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_imbalanced_Kudzu_maxent_global.tif")
Static_model_bioclim_imbalanced_Kudzu_rf_global <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_imbalanced_Kudzu_rf_global.tif")

# Kudzu -  worldclim balanced
Static_model_worldclim_balanced_Kudzu_gbm_1000km <- raster("./Results_all_predictiction_rasters/Static_model_worldclim_balanced_Kudzu_gbm_1000km.tif")
Static_model_worldclim_balanced_Kudzu_maxent_1000km <- raster("./Results_all_predictiction_rasters/Static_model_worldclim_balanced_Kudzu_maxent_1000km.tif")
Static_model_worldclim_balanced_Kudzu_rf_1000km <- raster("./Results_all_predictiction_rasters/Static_model_worldclim_balanced_Kudzu_rf_1000km.tif")

Static_model_worldclim_balanced_Kudzu_gbm_global <- raster("./Results_all_predictiction_rasters/Static_model_worldclim_balanced_Kudzu_gbm_global.tif")
Static_model_worldclim_balanced_Kudzu_maxent_global <- raster("./Results_all_predictiction_rasters/Static_model_worldclim_balanced_Kudzu_maxent_global.tif")
Static_model_worldclim_balanced_Kudzu_rf_global <- raster("./Results_all_predictiction_rasters/Static_model_worldclim_balanced_Kudzu_rf_global.tif")

#____________________________________________________________________________________________________________________________________

# Ladybird -  bioclim balanced
Static_model_bioclim_balanced_Ladybird_gbm_1000km <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_balanced_Ladybird_gbm_1000km.tif")
Static_model_bioclim_balanced_Ladybird_maxent_1000km <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_balanced_Ladybird_maxent_1000km.tif")
Static_model_bioclim_balanced_Ladybird_rf_1000km <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_balanced_Ladybird_rf_1000km.tif")

Static_model_bioclim_balanced_Ladybird_gbm_global <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_balanced_Ladybird_gbm_global.tif")
Static_model_bioclim_balanced_Ladybird_maxent_global <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_balanced_Ladybird_maxent_global.tif")
Static_model_bioclim_balanced_Ladybird_rf_global <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_balanced_Ladybird_rf_global.tif")

# Ladybird -  bioclim imbalanced
Static_model_bioclim_imbalanced_Ladybird_gbm_1000km <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_imbalanced_Ladybird_gbm_1000km.tif")
Static_model_bioclim_imbalanced_Ladybird_maxent_1000km <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_imbalanced_Ladybird_maxent_1000km.tif")
Static_model_bioclim_imbalanced_Ladybird_rf_1000km <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_imbalanced_Ladybird_rf_1000km.tif")

Static_model_bioclim_imbalanced_Ladybird_gbm_global <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_imbalanced_Ladybird_gbm_global.tif")
Static_model_bioclim_imbalanced_Ladybird_maxent_global <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_imbalanced_Ladybird_maxent_global.tif")
Static_model_bioclim_imbalanced_Ladybird_rf_global <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_imbalanced_Ladybird_rf_global.tif")

# Ladybird -  worldclim balanced
Static_model_worldclim_balanced_Ladybird_gbm_1000km <- raster("./Results_all_predictiction_rasters/Static_model_worldclim_balanced_Ladybird_gbm_1000km.tif")
Static_model_worldclim_balanced_Ladybird_maxent_1000km <- raster("./Results_all_predictiction_rasters/Static_model_worldclim_balanced_Ladybird_maxent_1000km.tif")
Static_model_worldclim_balanced_Ladybird_rf_1000km <- raster("./Results_all_predictiction_rasters/Static_model_worldclim_balanced_Ladybird_rf_1000km.tif")

Static_model_worldclim_balanced_Ladybird_gbm_global <- raster("./Results_all_predictiction_rasters/Static_model_worldclim_balanced_Ladybird_gbm_global.tif")
Static_model_worldclim_balanced_Ladybird_maxent_global <- raster("./Results_all_predictiction_rasters/Static_model_worldclim_balanced_Ladybird_maxent_global.tif")
Static_model_worldclim_balanced_Ladybird_rf_global <- raster("./Results_all_predictiction_rasters/Static_model_worldclim_balanced_Ladybird_rf_global.tif")

#____________________________________________________________________________________________________________________________________

# Parakeet -  bioclim balanced
Static_model_bioclim_balanced_Parakeet_gbm_1000km <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_balanced_Parakeet_gbm_1000km.tif")
Static_model_bioclim_balanced_Parakeet_maxent_1000km <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_balanced_Parakeet_maxent_1000km.tif")
Static_model_bioclim_balanced_Parakeet_rf_1000km <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_balanced_Parakeet_rf_1000km.tif")

Static_model_bioclim_balanced_Parakeet_gbm_global <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_balanced_Parakeet_gbm_global.tif")
Static_model_bioclim_balanced_Parakeet_maxent_global <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_balanced_Parakeet_maxent_global.tif")
Static_model_bioclim_balanced_Parakeet_rf_global <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_balanced_Parakeet_rf_global.tif")

# Parakeet -  bioclim imbalanced
Static_model_bioclim_imbalanced_Parakeet_gbm_1000km <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_imbalanced_Parakeet_gbm_1000km.tif")
Static_model_bioclim_imbalanced_Parakeet_maxent_1000km <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_imbalanced_Parakeet_maxent_1000km.tif")
Static_model_bioclim_imbalanced_Parakeet_rf_1000km <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_imbalanced_Parakeet_rf_1000km.tif")

Static_model_bioclim_imbalanced_Parakeet_gbm_global <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_imbalanced_Parakeet_gbm_global.tif")
Static_model_bioclim_imbalanced_Parakeet_maxent_global <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_imbalanced_Parakeet_maxent_global.tif")
Static_model_bioclim_imbalanced_Parakeet_rf_global <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_imbalanced_Parakeet_rf_global.tif")

# Parakeet -  worldclim balanced
Static_model_worldclim_balanced_Parakeet_gbm_1000km <- raster("./Results_all_predictiction_rasters/Static_model_worldclim_balanced_Parakeet_gbm_1000km.tif")
Static_model_worldclim_balanced_Parakeet_maxent_1000km <- raster("./Results_all_predictiction_rasters/Static_model_worldclim_balanced_Parakeet_maxent_1000km.tif")
Static_model_worldclim_balanced_Parakeet_rf_1000km <- raster("./Results_all_predictiction_rasters/Static_model_worldclim_balanced_Parakeet_rf_1000km.tif")

Static_model_worldclim_balanced_Parakeet_gbm_global <- raster("./Results_all_predictiction_rasters/Static_model_worldclim_balanced_Parakeet_gbm_global.tif")
Static_model_worldclim_balanced_Parakeet_maxent_global <- raster("./Results_all_predictiction_rasters/Static_model_worldclim_balanced_Parakeet_maxent_global.tif")
Static_model_worldclim_balanced_Parakeet_rf_global <- raster("./Results_all_predictiction_rasters/Static_model_worldclim_balanced_Parakeet_rf_global.tif")


```

#### 1000km {.tabset .tabset-pills}

##### Boar {.tabset .tabset-pills}

###### DL
```{r echo=FALSE}

plot( normalize_raster( DL_Boar_1000km ) , main = "Boar - Deep Learning " ) 

```

###### Bio_bal
```{r echo=FALSE}

plot( normalize_raster( Static_model_bioclim_balanced_Boar_gbm_1000km )  , main = "Boar - GBM " ) 
plot( normalize_raster( Static_model_bioclim_balanced_Boar_maxent_1000km )  , main = "Boar - MaxEnt " ) 
plot( normalize_raster( Static_model_bioclim_balanced_Boar_rf_1000km )  , main = "Boar - RF " ) 

```

###### Bio_imbal
```{r echo=FALSE}

plot( normalize_raster( Static_model_bioclim_imbalanced_Boar_gbm_1000km )  , main = "Boar - GBM " ) 
plot( normalize_raster( Static_model_bioclim_imbalanced_Boar_maxent_1000km )  , main = "Boar - MaxEnt " ) 
plot( normalize_raster( Static_model_bioclim_imbalanced_Boar_rf_1000km  ) , main = "Boar - RF " ) 

```

###### WC_bal
```{r echo=FALSE}

plot( normalize_raster( Static_model_worldclim_balanced_Boar_gbm_1000km )  , main = "Boar - GBM " ) 
plot( normalize_raster( Static_model_worldclim_balanced_Boar_maxent_1000km )  , main = "Boar - MaxEnt " ) 
plot( normalize_raster( Static_model_worldclim_balanced_Boar_rf_1000km )  , main = "Boar - RF " ) 

```

##### Kudzu {.tabset .tabset-pills}

###### DL
```{r echo=FALSE}

plot( normalize_raster( DL_Kudzu_1000km )  , main = "Kudzu - Deep Learning " ) 

```

###### Bio_bal
```{r echo=FALSE}

plot( normalize_raster( Static_model_bioclim_balanced_Kudzu_gbm_1000km )  , main = "Kudzu - GBM " ) 
plot( normalize_raster( Static_model_bioclim_balanced_Kudzu_maxent_1000km )  , main = "Kudzu - MaxEnt " ) 
plot( normalize_raster( Static_model_bioclim_balanced_Kudzu_rf_1000km )  , main = "Kudzu - RF " ) 

```

###### Bio_imbal
```{r echo=FALSE}

plot( normalize_raster( Static_model_bioclim_imbalanced_Kudzu_gbm_1000km )  , main = "Kudzu - GBM " ) 
plot( normalize_raster( Static_model_bioclim_imbalanced_Kudzu_maxent_1000km )  , main = "Kudzu - MaxEnt " ) 
plot( normalize_raster( Static_model_bioclim_imbalanced_Kudzu_rf_1000km )  , main = "Kudzu - RF " ) 

```

###### WC_bal
```{r echo=FALSE}

plot( normalize_raster( Static_model_worldclim_balanced_Kudzu_gbm_1000km )  , main = "Kudzu - GBM " ) 
plot( normalize_raster( Static_model_worldclim_balanced_Kudzu_maxent_1000km )  , main = "Kudzu - MaxEnt " ) 
plot( normalize_raster( Static_model_worldclim_balanced_Kudzu_rf_1000km )  , main = "Kudzu - RF " ) 

```


##### Ladybird {.tabset .tabset-pills}

###### DL
```{r echo=FALSE}

plot( normalize_raster( DL_Ladybird_1000km )  , main = "Ladybird - Deep Learning " ) 

```

###### Bio_bal
```{r echo=FALSE}

plot( normalize_raster( Static_model_bioclim_balanced_Ladybird_gbm_1000km )  , main = "Ladybird - GBM " ) 
plot( normalize_raster( Static_model_bioclim_balanced_Ladybird_maxent_1000km )  , main = "Ladybird - MaxEnt " ) 
plot( normalize_raster( Static_model_bioclim_balanced_Ladybird_rf_1000km )  , main = "Ladybird - RF " ) 

```

###### Bio_imbal
```{r echo=FALSE}

plot( normalize_raster( Static_model_bioclim_imbalanced_Ladybird_gbm_1000km )  , main = "Ladybird - GBM " ) 
plot( normalize_raster( Static_model_bioclim_imbalanced_Ladybird_maxent_1000km )  , main = "Ladybird - MaxEnt " ) 
plot( normalize_raster( Static_model_bioclim_imbalanced_Ladybird_rf_1000km )  , main = "Ladybird - RF " ) 

```

###### WC_bal
```{r echo=FALSE}

plot( normalize_raster( Static_model_worldclim_balanced_Ladybird_gbm_1000km )  , main = "Ladybird - GBM " ) 
plot( normalize_raster( Static_model_worldclim_balanced_Ladybird_maxent_1000km )  , main = "Ladybird - MaxEnt " ) 
plot( normalize_raster( Static_model_worldclim_balanced_Ladybird_rf_1000km )  , main = "Ladybird - RF " ) 

```


##### Parakeet {.tabset .tabset-pills}

###### DL
```{r echo=FALSE}

plot( normalize_raster( DL_Parakeet_1000km )  , main = "Parakeet - Deep Learning " ) 

```

###### Bio_bal
```{r echo=FALSE}

plot( normalize_raster( Static_model_bioclim_balanced_Parakeet_gbm_1000km )  , main = "Parakeet - GBM " ) 
plot( normalize_raster( Static_model_bioclim_balanced_Parakeet_maxent_1000km )  , main = "Parakeet - MaxEnt " ) 
plot( normalize_raster( Static_model_bioclim_balanced_Parakeet_rf_1000km )  , main = "Parakeet - RF " ) 

```

###### Bio_imbal
```{r echo=FALSE}

plot( normalize_raster( Static_model_bioclim_imbalanced_Parakeet_gbm_1000km )  , main = "Parakeet - GBM " ) 
plot( normalize_raster( Static_model_bioclim_imbalanced_Parakeet_maxent_1000km )  , main = "Parakeet - MaxEnt " ) 
plot( normalize_raster( Static_model_bioclim_imbalanced_Parakeet_rf_1000km )  , main = "Parakeet - RF " ) 

```

###### WC_bal
```{r echo=FALSE}

plot( normalize_raster( Static_model_worldclim_balanced_Parakeet_gbm_1000km )  , main = "Parakeet - GBM " ) 
plot( normalize_raster( Static_model_worldclim_balanced_Parakeet_maxent_1000km )  , main = "Parakeet - MaxEnt " ) 
plot( normalize_raster( Static_model_worldclim_balanced_Parakeet_rf_1000km  ) , main = "Parakeet - RF " ) 

```

#### {-}

#### Global {.tabset .tabset-pills}

##### Boar {.tabset .tabset-pills}

###### DL
```{r echo=FALSE}

plot( normalize_raster( DL_Boar_global )  , main = "Boar - Deep Learning " ) 

```

###### Bio_bal
```{r echo=FALSE}

plot( normalize_raster( Static_model_bioclim_balanced_Boar_gbm_global )  , main = "Boar - GBM " ) 
plot( normalize_raster( Static_model_bioclim_balanced_Boar_maxent_global )  , main = "Boar - MaxEnt " ) 
plot( normalize_raster( Static_model_bioclim_balanced_Boar_rf_global )  , main = "Boar - RF " ) 

```

###### Bio_imbal
```{r echo=FALSE}

plot( normalize_raster( Static_model_bioclim_imbalanced_Boar_gbm_global )  , main = "Boar - GBM " ) 
plot( normalize_raster( Static_model_bioclim_imbalanced_Boar_maxent_global )  , main = "Boar - MaxEnt " ) 
plot( normalize_raster( Static_model_bioclim_imbalanced_Boar_rf_global )  , main = "Boar - RF " ) 

```

###### WC_bal
```{r echo=FALSE}

plot( normalize_raster( Static_model_worldclim_balanced_Boar_gbm_global )  , main = "Boar - GBM " ) 
plot( normalize_raster( Static_model_worldclim_balanced_Boar_maxent_global )  , main = "Boar - MaxEnt " ) 
plot( normalize_raster( Static_model_worldclim_balanced_Boar_rf_global )  , main = "Boar - RF " ) 

```

##### Kudzu {.tabset .tabset-pills}

###### DL
```{r echo=FALSE}

plot( normalize_raster( DL_Kudzu_global )  , main = "Kudzu - Deep Learning " ) 

```

###### Bio_bal
```{r echo=FALSE}

plot( normalize_raster( Static_model_bioclim_balanced_Kudzu_gbm_global )  , main = "Kudzu - GBM " ) 
plot( normalize_raster( Static_model_bioclim_balanced_Kudzu_maxent_global )  , main = "Kudzu - MaxEnt " ) 
plot( normalize_raster( Static_model_bioclim_balanced_Kudzu_rf_global )  , main = "Kudzu - RF " ) 

```

###### Bio_imbal
```{r echo=FALSE}

plot( normalize_raster( Static_model_bioclim_imbalanced_Kudzu_gbm_global )  , main = "Kudzu - GBM " ) 
plot( normalize_raster( Static_model_bioclim_imbalanced_Kudzu_maxent_global  ) , main = "Kudzu - MaxEnt " ) 
plot( normalize_raster( Static_model_bioclim_imbalanced_Kudzu_rf_global )  , main = "Kudzu - RF " ) 

```

###### WC_bal
```{r echo=FALSE}

plot( normalize_raster( Static_model_worldclim_balanced_Kudzu_gbm_global )  , main = "Kudzu - GBM " ) 
plot( normalize_raster( Static_model_worldclim_balanced_Kudzu_maxent_global )  , main = "Kudzu - MaxEnt " ) 
plot( normalize_raster( Static_model_worldclim_balanced_Kudzu_rf_global )  , main = "Kudzu - RF " ) 

```


##### Ladybird {.tabset .tabset-pills}

###### DL
```{r echo=FALSE}

plot( normalize_raster( DL_Ladybird_global )  , main = "Ladybird - Deep Learning " ) 

```

###### Bio_bal
```{r echo=FALSE}

plot( normalize_raster( Static_model_bioclim_balanced_Ladybird_gbm_global )  , main = "Ladybird - GBM " ) 
plot( normalize_raster( Static_model_bioclim_balanced_Ladybird_maxent_global ) , main = "Ladybird - MaxEnt " ) 
plot( normalize_raster( Static_model_bioclim_balanced_Ladybird_rf_global )  , main = "Ladybird - RF " ) 

```

###### Bio_imbal
```{r echo=FALSE}

plot( normalize_raster( Static_model_bioclim_imbalanced_Ladybird_gbm_global )  , main = "Ladybird - GBM " ) 
plot( normalize_raster( Static_model_bioclim_imbalanced_Ladybird_maxent_global )  , main = "Ladybird - MaxEnt " ) 
plot( normalize_raster( Static_model_bioclim_imbalanced_Ladybird_rf_global )  , main = "Ladybird - RF " ) 

```

###### WC_bal
```{r echo=FALSE}

plot( normalize_raster( Static_model_worldclim_balanced_Ladybird_gbm_global )  , main = "Ladybird - GBM " ) 
plot( normalize_raster( Static_model_worldclim_balanced_Ladybird_maxent_global )  , main = "Ladybird - MaxEnt " ) 
plot( normalize_raster( Static_model_worldclim_balanced_Ladybird_rf_global )  , main = "Ladybird - RF " ) 

```


##### Parakeet {.tabset .tabset-pills}

###### DL
```{r echo=FALSE}

plot( normalize_raster( DL_Parakeet_global )  , main = "Parakeet - Deep Learning " ) 

```

###### Bio_bal
```{r echo=FALSE}

plot( normalize_raster( Static_model_bioclim_balanced_Parakeet_gbm_global )  , main = "Parakeet - GBM " ) 
plot( normalize_raster( Static_model_bioclim_balanced_Parakeet_maxent_global )  , main = "Parakeet - MaxEnt " ) 
plot( normalize_raster( Static_model_bioclim_balanced_Parakeet_rf_global ) , main = "Parakeet - RF " ) 

```

###### Bio_imbal
```{r echo=FALSE}

plot( normalize_raster( Static_model_bioclim_imbalanced_Parakeet_gbm_global )  , main = "Parakeet - GBM " ) 
plot( normalize_raster( Static_model_bioclim_imbalanced_Parakeet_maxent_global )  , main = "Parakeet - MaxEnt " ) 
plot( normalize_raster( Static_model_bioclim_imbalanced_Parakeet_rf_global )  , main = "Parakeet - RF " ) 

```

###### WC_bal
```{r echo=FALSE}

plot( normalize_raster( Static_model_worldclim_balanced_Parakeet_gbm_global )  , main = "Parakeet - GBM " ) 
plot( normalize_raster( Static_model_worldclim_balanced_Parakeet_maxent_global )  , main = "Parakeet - MaxEnt " ) 
plot( normalize_raster( Static_model_worldclim_balanced_Parakeet_rf_global )  , main = "Parakeet - RF " ) 

```

#### {-}

#### P/A {.tabset .tabset-pills}


```{r echo=FALSE}

# Monkeyflower

##############################
# DL Models
##############################


DL_Monkeyflower_donut <- raster("./Results_all_predictiction_rasters/DL_Monkeyflower.tif") 



##############################
# Static Models
##############################


Static_model_bioclim_balanced_Monkeyflower_gbm_donut <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_balanced_Monkeyflower_gbm_donut.tif")
Static_model_bioclim_balanced_Monkeyflower_maxent_donut <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_balanced_Monkeyflower_maxent_donut.tif")
Static_model_bioclim_balanced_Monkeyflower_rf_donut <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_balanced_Monkeyflower_rf_donut.tif")


Static_model_bioclim_imbalanced_Monkeyflower_gbm_donut <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_imbalanced_Monkeyflower_gbm_donut.tif")
Static_model_bioclim_imbalanced_Monkeyflower_maxent_donut <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_imbalanced_Monkeyflower_maxent_donut.tif")
Static_model_bioclim_imbalanced_Monkeyflower_rf_donut <- raster("./Results_all_predictiction_rasters/Static_model_bioclim_imbalanced_Monkeyflower_rf_donut.tif")



Static_model_worldclim_balanced_Monkeyflower_gbm_donut <- raster("./Results_all_predictiction_rasters/Static_model_worldclim_balanced_Monkeyflower_gbm_donut.tif")
Static_model_worldclim_balanced_Monkeyflower_maxent_donut <- raster("./Results_all_predictiction_rasters/Static_model_worldclim_balanced_Monkeyflower_maxent_donut.tif")
Static_model_worldclim_balanced_Monkeyflower_rf_donut <- raster("./Results_all_predictiction_rasters/Static_model_worldclim_balanced_Monkeyflower_rf_donut.tif")

#____________________________________________________________________________________________________________________________________


DL_Monkeyflower_donut<- crop( DL_Monkeyflower_donut , Static_model_bioclim_balanced_Monkeyflower_gbm_donut )


```



##### DL
```{r echo=FALSE}

plot( normalize_raster( DL_Monkeyflower_donut )  , main = "Monkeyflower - Deep Learning " , xlim = c( -125.156250 , -110.917969 ) , ylim = c( 32.287133 , 49.439557 )  ) 

```

##### Bio_bal
```{r echo=FALSE}

plot( normalize_raster( Static_model_bioclim_balanced_Monkeyflower_gbm_donut )  , main = "Monkeyflower - GBM " , xlim = c( -125.156250 , -110.917969 ) , ylim = c( 32.287133 , 49.439557 ) ) 
plot( normalize_raster( Static_model_bioclim_balanced_Monkeyflower_maxent_donut )  , main = "Monkeyflower - MaxEnt " , xlim = c( -125.156250 , -110.917969 ) , ylim = c( 32.287133 , 49.439557 ) ) 
plot( normalize_raster( Static_model_bioclim_balanced_Monkeyflower_rf_donut ) , main = "Monkeyflower - RF " , xlim = c( -125.156250 , -110.917969 ) , ylim = c( 32.287133 , 49.439557 ) ) 

```

##### Bio_imbal
```{r echo=FALSE}

plot( normalize_raster( Static_model_bioclim_imbalanced_Monkeyflower_gbm_donut )  , main = "Monkeyflower - GBM " , xlim = c( -125.156250 , -110.917969 ) , ylim = c( 32.287133 , 49.439557 )  ) 
plot( normalize_raster( Static_model_bioclim_imbalanced_Monkeyflower_maxent_donut )  , main = "Monkeyflower - MaxEnt " , xlim = c( -125.156250 , -110.917969 ) , ylim = c( 32.287133 , 49.439557 )  ) 
plot( normalize_raster( Static_model_bioclim_imbalanced_Monkeyflower_rf_donut )  , main = "Monkeyflower - RF " , xlim = c( -125.156250 , -110.917969 ) , ylim = c( 32.287133 , 49.439557 )  ) 

```

##### WC_bal
```{r echo=FALSE}

plot( normalize_raster( Static_model_worldclim_balanced_Monkeyflower_gbm_donut )  , main = "Monkeyflower - GBM " , xlim = c( -125.156250 , -110.917969 ) , ylim = c( 32.287133 , 49.439557 )  ) 
plot( normalize_raster( Static_model_worldclim_balanced_Monkeyflower_maxent_donut )  , main = "Monkeyflower - MaxEnt " , xlim = c( -125.156250 , -110.917969 ) , ylim = c( 32.287133 , 49.439557 ) ) 
plot( normalize_raster( Static_model_worldclim_balanced_Monkeyflower_rf_donut )  , main = "Monkeyflower - RF " , xlim = c( -125.156250 , -110.917969 ) , ylim = c( 32.287133 , 49.439557 ) ) 

```

#### {-}

### {-}


### Prediction comparisons: deep-learning v. static machine learning {.tabset .tabset-pills}
```{r include=FALSE}

#library(pROC)

# 1000km  ________________________________________________________________________________________________________________________________________________________

# Boar

final_Boar_1000km <- roc( data.frame( read_csv( "./Results_deep_learning/Best_models/Time_series_best_model_true_values_Boar_1000km.csv" ,  col_names = FALSE ) )$X1 , 
                       data.frame( read_csv( "./Results_deep_learning/Best_models/Time_series_best_model_test_predictions_Boar_1000km.csv",  col_names = FALSE ) )$X1 ) 
# Calculate sens_spec
# determine the best threshold
Boar_dl_th_1000km <- which(final_Boar_1000km$sensitivities + final_Boar_1000km$specificities == max(final_Boar_1000km$sensitivities + final_Boar_1000km$specificities), arr.ind = TRUE)
final_Boar_1000km$thresholds[[Boar_dl_th_1000km]]

# Kudzu

final_Kudzu_1000km <- roc( data.frame( read_csv( "./Results_deep_learning/Best_models/Time_series_best_model_true_values_Kudzu_1000km.csv" ,  col_names = FALSE ) )$X1 , 
                       data.frame( read_csv( "./Results_deep_learning/Best_models/Time_series_best_model_test_predictions_Kudzu_1000km.csv",  col_names = FALSE ) )$X1 ) 
# Calculate sens_spec
final_Kudzu_1000km$sensitivities + final_Kudzu_1000km$specificities
max( final_Kudzu_1000km$sensitivities + final_Kudzu_1000km$specificities )
# determine the best threshold
Kudzu_dl_th_1000km <- which(final_Kudzu_1000km$sensitivities + final_Kudzu_1000km$specificities == max(final_Kudzu_1000km$sensitivities + final_Kudzu_1000km$specificities), arr.ind = TRUE)
final_Kudzu_1000km$thresholds[[Kudzu_dl_th_1000km]]

# Ladybird

final_Ladybird_1000km <- roc( data.frame( read_csv( "./Results_deep_learning/Best_models/Time_series_best_model_true_values_Ladybird_1000km.csv" ,  col_names = FALSE ) )$X1 , 
                       data.frame( read_csv( "./Results_deep_learning/Best_models/Time_series_best_model_test_predictions_Ladybird_1000km.csv",  col_names = FALSE ) )$X1 ) 
# Calculate sens_spec
# determine the best threshold
Ladybird_dl_th_1000km <- which(final_Ladybird_1000km$sensitivities + final_Ladybird_1000km$specificities == max(final_Ladybird_1000km$sensitivities + final_Ladybird_1000km$specificities), arr.ind = TRUE)
final_Ladybird_1000km$thresholds[[Ladybird_dl_th_1000km]]

# Parakeet

final_Parakeet_1000km <- roc( data.frame( read_csv( "./Results_deep_learning/Best_models/Time_series_best_model_true_values_Parakeet_1000km.csv" ,  col_names = FALSE ) )$X1 , 
                       data.frame( read_csv( "./Results_deep_learning/Best_models/Time_series_best_model_test_predictions_Parakeet_1000km.csv",  col_names = FALSE ) )$X1 ) 
# Calculate sens_spec
# determine the best threshold
Parakeet_dl_th_1000km <- which(final_Parakeet_1000km$sensitivities + final_Parakeet_1000km$specificities == max(final_Parakeet_1000km$sensitivities + final_Parakeet_1000km$specificities), arr.ind = TRUE)
final_Parakeet_1000km$thresholds[[Parakeet_dl_th_1000km]]



# global  ________________________________________________________________________________________________________________________________________________________

# Boar

final_Boar_global <- roc( data.frame( read_csv( "./Results_deep_learning/Best_models/Time_series_best_model_true_values_Boar_global.csv" ,  col_names = FALSE ) )$X1 , 
                                      data.frame( read_csv( "./Results_deep_learning/Best_models/Time_series_best_model_test_predictions_Boar_global.csv",  col_names = FALSE ) )$X1 ) 
# Calculate sens_spec
# determine the best threshold
Boar_dl_th_global <- which(final_Boar_global$sensitivities + final_Boar_global$specificities == max(final_Boar_global$sensitivities + final_Boar_global$specificities), arr.ind = TRUE)
final_Boar_global$thresholds[[Boar_dl_th_global]]

# Kudzu

final_Kudzu_global <- roc( data.frame( read_csv( "./Results_deep_learning/Best_models/Time_series_best_model_true_values_Kudzu_global.csv" ,  col_names = FALSE ) )$X1 , 
                                       data.frame( read_csv( "./Results_deep_learning/Best_models/Time_series_best_model_test_predictions_Kudzu_global.csv",  col_names = FALSE ) )$X1 ) 
# Calculate sens_spec
# determine the best threshold
Kudzu_dl_th_global <- which(final_Kudzu_global$sensitivities + final_Kudzu_global$specificities == max(final_Kudzu_global$sensitivities + final_Kudzu_global$specificities), arr.ind = TRUE)
final_Kudzu_global$thresholds[[Kudzu_dl_th_global]]

# Ladybird

final_Ladybird_global <- roc( data.frame(read_csv( "./Results_deep_learning/Best_models/Time_series_best_model_true_values_Ladybird_global.csv" ,  col_names = FALSE ) )$X1 , 
                                          data.frame( read_csv( "./Results_deep_learning/Best_models/Time_series_best_model_test_predictions_Ladybird_global.csv",  col_names = FALSE ) )$X1 ) 
# Calculate sens_spec
# determine the best threshold
Ladybird_dl_th_global <- which(final_Ladybird_global$sensitivities + final_Ladybird_global$specificities == max(final_Ladybird_global$sensitivities + final_Ladybird_global$specificities), arr.ind = TRUE)
final_Ladybird_global$thresholds[[Ladybird_dl_th_global]]

# Parakeet

final_Parakeet_global <- roc( data.frame(read_csv( "./Results_deep_learning/Best_models/Time_series_best_model_true_values_Parakeet_global.csv" ,  col_names = FALSE ) )$X1 , 
                                          data.frame( read_csv( "./Results_deep_learning/Best_models/Time_series_best_model_test_predictions_Parakeet_global.csv",  col_names = FALSE ) )$X1 ) 
# Calculate sens_spec
# determine the best threshold
Parakeet_dl_th_global <- which(final_Parakeet_global$sensitivities + final_Parakeet_global$specificities == max(final_Parakeet_global$sensitivities + final_Parakeet_global$specificities), arr.ind = TRUE)
final_Parakeet_global$thresholds[[Parakeet_dl_th_global]]

#___________________________________________________________


DL_Boar_1000km_th <-  ( ( DL_Boar_1000km > final_Boar_1000km$thresholds[[Boar_dl_th_1000km]] ) * 2 )
DL_Kudzu_1000km_th <-  ( ( DL_Kudzu_1000km > final_Kudzu_1000km$thresholds[[Kudzu_dl_th_1000km]] ) * 2 )
DL_Ladybird_1000km_th <-  ( ( DL_Ladybird_1000km > final_Ladybird_1000km$thresholds[[Ladybird_dl_th_1000km]] ) * 2 )
DL_Parakeet_1000km_th <-  ( ( DL_Parakeet_1000km > final_Parakeet_1000km$thresholds[[Parakeet_dl_th_1000km]] ) * 2 )

DL_Boar_global_th <-  ( ( DL_Boar_global > final_Boar_global$thresholds[[Boar_dl_th_global]] ) * 2 )
DL_Kudzu_global_th <-  ( ( DL_Kudzu_global > final_Kudzu_global$thresholds[[Kudzu_dl_th_global]] ) * 2 )
DL_Ladybird_global_th <-  ( ( DL_Ladybird_global > final_Ladybird_global$thresholds[[Ladybird_dl_th_global]] ) * 2 )
DL_Parakeet_global_th <-  ( ( DL_Parakeet_global > final_Parakeet_global$thresholds[[Parakeet_dl_th_global]] ) * 2 )

# Boar -  bioclim balanced
Static_model_bioclim_balanced_Boar_gbm_1000km_th <- ( crop( Static_model_bioclim_balanced_Boar_gbm_1000km , DL_Boar_1000km_th )  > Static_model_bioclim_balanced_results_Boar_1000km[1,2] )
Static_model_bioclim_balanced_Boar_maxent_1000km_th <- ( crop( Static_model_bioclim_balanced_Boar_maxent_1000km , DL_Boar_1000km_th )  > Static_model_bioclim_balanced_results_Boar_1000km[2,2] )
Static_model_bioclim_balanced_Boar_rf_1000km_th <- ( crop( Static_model_bioclim_balanced_Boar_rf_1000km , DL_Boar_1000km_th )  > Static_model_bioclim_balanced_results_Boar_1000km[3,2] )

Static_model_bioclim_balanced_Boar_gbm_global_th <- ( crop( Static_model_bioclim_balanced_Boar_gbm_global , DL_Boar_global_th )  > Static_model_bioclim_balanced_results_Boar_global[1,2] )
Static_model_bioclim_balanced_Boar_maxent_global_th <- ( crop( Static_model_bioclim_balanced_Boar_maxent_global , DL_Boar_global_th )  > Static_model_bioclim_balanced_results_Boar_global[2,2] )
Static_model_bioclim_balanced_Boar_rf_global_th <- ( crop( Static_model_bioclim_balanced_Boar_rf_global , DL_Boar_global_th )  > Static_model_bioclim_balanced_results_Boar_global[3,2] )

# Boar -  bioclim imbalanced
Static_model_bioclim_imbalanced_Boar_gbm_1000km_th <- ( crop( Static_model_bioclim_imbalanced_Boar_gbm_1000km , DL_Boar_1000km_th )  > Static_model_bioclim_imbalanced_results_Boar_1000km[1,2] )
Static_model_bioclim_imbalanced_Boar_maxent_1000km_th <- ( crop( Static_model_bioclim_imbalanced_Boar_maxent_1000km , DL_Boar_1000km_th )  > Static_model_bioclim_imbalanced_results_Boar_1000km[2,2] )
Static_model_bioclim_imbalanced_Boar_rf_1000km_th <- ( crop( Static_model_bioclim_imbalanced_Boar_rf_1000km , DL_Boar_1000km_th )  > Static_model_bioclim_imbalanced_results_Boar_1000km[3,2] )

Static_model_bioclim_imbalanced_Boar_gbm_global_th <- ( crop( Static_model_bioclim_imbalanced_Boar_gbm_global , DL_Boar_global_th )  > Static_model_bioclim_imbalanced_results_Boar_global[1,2] )
Static_model_bioclim_imbalanced_Boar_maxent_global_th <- ( crop( Static_model_bioclim_imbalanced_Boar_maxent_global , DL_Boar_global_th )  > Static_model_bioclim_imbalanced_results_Boar_global[2,2] )
Static_model_bioclim_imbalanced_Boar_rf_global_th <- ( crop( Static_model_bioclim_imbalanced_Boar_rf_global , DL_Boar_global_th )  > Static_model_bioclim_imbalanced_results_Boar_global[3,2] )

# Boar -  worldclim balanced
Static_model_worldclim_balanced_Boar_gbm_1000km_th <- ( crop( Static_model_worldclim_balanced_Boar_gbm_1000km , DL_Boar_1000km_th )  > Static_model_worldclim_balanced_results_Boar_1000km[1,2] )
Static_model_worldclim_balanced_Boar_maxent_1000km_th <- ( crop( Static_model_worldclim_balanced_Boar_maxent_1000km , DL_Boar_1000km_th )  > Static_model_worldclim_balanced_results_Boar_1000km[2,2] )
Static_model_worldclim_balanced_Boar_rf_1000km_th <- ( crop( Static_model_worldclim_balanced_Boar_rf_1000km , DL_Boar_1000km_th )  > Static_model_worldclim_balanced_results_Boar_1000km[3,2] )

Static_model_worldclim_balanced_Boar_gbm_global_th <- ( crop( Static_model_worldclim_balanced_Boar_gbm_global , DL_Boar_global_th )  > Static_model_worldclim_balanced_results_Boar_global[1,2] )
Static_model_worldclim_balanced_Boar_maxent_global_th <- ( crop( Static_model_worldclim_balanced_Boar_maxent_global , DL_Boar_global_th )  > Static_model_worldclim_balanced_results_Boar_global[2,2] )
Static_model_worldclim_balanced_Boar_rf_global_th <- ( crop( Static_model_worldclim_balanced_Boar_rf_global , DL_Boar_global_th )  > Static_model_worldclim_balanced_results_Boar_global[3,2] )

#_________________________________________________________________________

# Kudzu -  bioclim balanced
Static_model_bioclim_balanced_Kudzu_gbm_1000km_th <- ( crop( Static_model_bioclim_balanced_Kudzu_gbm_1000km , DL_Kudzu_1000km_th )  > Static_model_bioclim_balanced_results_Kudzu_1000km[1,2] )
Static_model_bioclim_balanced_Kudzu_maxent_1000km_th <- ( crop( Static_model_bioclim_balanced_Kudzu_maxent_1000km , DL_Kudzu_1000km_th )  > Static_model_bioclim_balanced_results_Kudzu_1000km[2,2] )
Static_model_bioclim_balanced_Kudzu_rf_1000km_th <- ( crop( Static_model_bioclim_balanced_Kudzu_rf_1000km , DL_Kudzu_1000km_th )  > Static_model_bioclim_balanced_results_Kudzu_1000km[3,2] )

Static_model_bioclim_balanced_Kudzu_gbm_global_th <- ( crop( Static_model_bioclim_balanced_Kudzu_gbm_global , DL_Kudzu_global_th )  > Static_model_bioclim_balanced_results_Kudzu_global[1,2] )
Static_model_bioclim_balanced_Kudzu_maxent_global_th <- ( crop( Static_model_bioclim_balanced_Kudzu_maxent_global , DL_Kudzu_global_th )  > Static_model_bioclim_balanced_results_Kudzu_global[2,2] )
Static_model_bioclim_balanced_Kudzu_rf_global_th <- ( crop( Static_model_bioclim_balanced_Kudzu_rf_global , DL_Kudzu_global_th )  > Static_model_bioclim_balanced_results_Kudzu_global[3,2] )

# Kudzu -  bioclim imbalanced
Static_model_bioclim_imbalanced_Kudzu_gbm_1000km_th <- ( crop( Static_model_bioclim_imbalanced_Kudzu_gbm_1000km , DL_Kudzu_1000km_th )  > Static_model_bioclim_imbalanced_results_Kudzu_1000km[1,2] )
Static_model_bioclim_imbalanced_Kudzu_maxent_1000km_th <- ( crop( Static_model_bioclim_imbalanced_Kudzu_maxent_1000km , DL_Kudzu_1000km_th )  > Static_model_bioclim_imbalanced_results_Kudzu_1000km[2,2] )
Static_model_bioclim_imbalanced_Kudzu_rf_1000km_th <- ( crop( Static_model_bioclim_imbalanced_Kudzu_rf_1000km , DL_Kudzu_1000km_th )  > Static_model_bioclim_imbalanced_results_Kudzu_1000km[3,2] )

Static_model_bioclim_imbalanced_Kudzu_gbm_global_th <- ( crop( Static_model_bioclim_imbalanced_Kudzu_gbm_global , DL_Kudzu_global_th )  > Static_model_bioclim_imbalanced_results_Kudzu_global[1,2] )
Static_model_bioclim_imbalanced_Kudzu_maxent_global_th <- ( crop( Static_model_bioclim_imbalanced_Kudzu_maxent_global , DL_Kudzu_global_th )  > Static_model_bioclim_imbalanced_results_Kudzu_global[2,2] )
Static_model_bioclim_imbalanced_Kudzu_rf_global_th <- ( crop( Static_model_bioclim_imbalanced_Kudzu_rf_global , DL_Kudzu_global_th )  > Static_model_bioclim_imbalanced_results_Kudzu_global[3,2] )

# Kudzu -  worldclim balanced
Static_model_worldclim_balanced_Kudzu_gbm_1000km_th <- ( crop( Static_model_worldclim_balanced_Kudzu_gbm_1000km , DL_Kudzu_1000km_th )  > Static_model_worldclim_balanced_results_Kudzu_1000km[1,2] )
Static_model_worldclim_balanced_Kudzu_maxent_1000km_th <- ( crop( Static_model_worldclim_balanced_Kudzu_maxent_1000km , DL_Kudzu_1000km_th )  > Static_model_worldclim_balanced_results_Kudzu_1000km[2,2] )
Static_model_worldclim_balanced_Kudzu_rf_1000km_th <- ( crop( Static_model_worldclim_balanced_Kudzu_rf_1000km , DL_Kudzu_1000km_th )  > Static_model_worldclim_balanced_results_Kudzu_1000km[3,2] )

Static_model_worldclim_balanced_Kudzu_gbm_global_th <- ( crop( Static_model_worldclim_balanced_Kudzu_gbm_global , DL_Kudzu_global_th )  > Static_model_worldclim_balanced_results_Kudzu_global[1,2] )
Static_model_worldclim_balanced_Kudzu_maxent_global_th <- ( crop( Static_model_worldclim_balanced_Kudzu_maxent_global , DL_Kudzu_global_th )  > Static_model_worldclim_balanced_results_Kudzu_global[2,2] )
Static_model_worldclim_balanced_Kudzu_rf_global_th <- ( crop( Static_model_worldclim_balanced_Kudzu_rf_global , DL_Kudzu_global_th )  > Static_model_worldclim_balanced_results_Kudzu_global[3,2] )

#_________________________________________________________________________

# Ladybird -  bioclim balanced
Static_model_bioclim_balanced_Ladybird_gbm_1000km_th <- ( crop( Static_model_bioclim_balanced_Ladybird_gbm_1000km , DL_Ladybird_1000km_th )  > Static_model_bioclim_balanced_results_Ladybird_1000km[1,2] )
Static_model_bioclim_balanced_Ladybird_maxent_1000km_th <- ( crop( Static_model_bioclim_balanced_Ladybird_maxent_1000km , DL_Ladybird_1000km_th )  > Static_model_bioclim_balanced_results_Ladybird_1000km[2,2] )
Static_model_bioclim_balanced_Ladybird_rf_1000km_th <- ( crop( Static_model_bioclim_balanced_Ladybird_rf_1000km , DL_Ladybird_1000km_th )  > Static_model_bioclim_balanced_results_Ladybird_1000km[3,2] )

Static_model_bioclim_balanced_Ladybird_gbm_global_th <- ( crop( Static_model_bioclim_balanced_Ladybird_gbm_global , DL_Ladybird_global_th )  > Static_model_bioclim_balanced_results_Ladybird_global[1,2] )
Static_model_bioclim_balanced_Ladybird_maxent_global_th <- ( crop( Static_model_bioclim_balanced_Ladybird_maxent_global , DL_Ladybird_global_th )  > Static_model_bioclim_balanced_results_Ladybird_global[2,2] )
Static_model_bioclim_balanced_Ladybird_rf_global_th <- ( crop( Static_model_bioclim_balanced_Ladybird_rf_global , DL_Ladybird_global_th )  > Static_model_bioclim_balanced_results_Ladybird_global[3,2] )

# Ladybird -  bioclim imbalanced
Static_model_bioclim_imbalanced_Ladybird_gbm_1000km_th <- ( crop( Static_model_bioclim_imbalanced_Ladybird_gbm_1000km , DL_Ladybird_1000km_th )  > Static_model_bioclim_imbalanced_results_Ladybird_1000km[1,2] )
Static_model_bioclim_imbalanced_Ladybird_maxent_1000km_th <- ( crop( Static_model_bioclim_imbalanced_Ladybird_maxent_1000km , DL_Ladybird_1000km_th )  > Static_model_bioclim_imbalanced_results_Ladybird_1000km[2,2] )
Static_model_bioclim_imbalanced_Ladybird_rf_1000km_th <- ( crop( Static_model_bioclim_imbalanced_Ladybird_rf_1000km , DL_Ladybird_1000km_th )  > Static_model_bioclim_imbalanced_results_Ladybird_1000km[3,2] )

Static_model_bioclim_imbalanced_Ladybird_gbm_global_th <- ( crop( Static_model_bioclim_imbalanced_Ladybird_gbm_global , DL_Ladybird_global_th )  > Static_model_bioclim_imbalanced_results_Ladybird_global[1,2] )
Static_model_bioclim_imbalanced_Ladybird_maxent_global_th <- ( crop( Static_model_bioclim_imbalanced_Ladybird_maxent_global , DL_Ladybird_global_th )  > Static_model_bioclim_imbalanced_results_Ladybird_global[2,2] )
Static_model_bioclim_imbalanced_Ladybird_rf_global_th <- ( crop( Static_model_bioclim_imbalanced_Ladybird_rf_global , DL_Ladybird_global_th )  > Static_model_bioclim_imbalanced_results_Ladybird_global[3,2] )

# Ladybird -  worldclim balanced
Static_model_worldclim_balanced_Ladybird_gbm_1000km_th <- ( crop( Static_model_worldclim_balanced_Ladybird_gbm_1000km , DL_Ladybird_1000km_th )  > Static_model_worldclim_balanced_results_Ladybird_1000km[1,2] )
Static_model_worldclim_balanced_Ladybird_maxent_1000km_th <- ( crop( Static_model_worldclim_balanced_Ladybird_maxent_1000km , DL_Ladybird_1000km_th )  > Static_model_worldclim_balanced_results_Ladybird_1000km[2,2] )
Static_model_worldclim_balanced_Ladybird_rf_1000km_th <- ( crop( Static_model_worldclim_balanced_Ladybird_rf_1000km , DL_Ladybird_1000km_th )  > Static_model_worldclim_balanced_results_Ladybird_1000km[3,2] )

Static_model_worldclim_balanced_Ladybird_gbm_global_th <- ( crop( Static_model_worldclim_balanced_Ladybird_gbm_global , DL_Ladybird_global_th )  > Static_model_worldclim_balanced_results_Ladybird_global[1,2] )
Static_model_worldclim_balanced_Ladybird_maxent_global_th <- ( crop( Static_model_worldclim_balanced_Ladybird_maxent_global , DL_Ladybird_global_th )  > Static_model_worldclim_balanced_results_Ladybird_global[2,2] )
Static_model_worldclim_balanced_Ladybird_rf_global_th <- ( crop( Static_model_worldclim_balanced_Ladybird_rf_global , DL_Ladybird_global_th )  > Static_model_worldclim_balanced_results_Ladybird_global[3,2] )

#_________________________________________________________________________

# Parakeet -  bioclim balanced
Static_model_bioclim_balanced_Parakeet_gbm_1000km_th <- ( crop( Static_model_bioclim_balanced_Parakeet_gbm_1000km , DL_Parakeet_1000km_th )  > Static_model_bioclim_balanced_results_Parakeet_1000km[1,2] )
Static_model_bioclim_balanced_Parakeet_maxent_1000km_th <- ( crop( Static_model_bioclim_balanced_Parakeet_maxent_1000km , DL_Parakeet_1000km_th )  > Static_model_bioclim_balanced_results_Parakeet_1000km[2,2] )
Static_model_bioclim_balanced_Parakeet_rf_1000km_th <- ( crop( Static_model_bioclim_balanced_Parakeet_rf_1000km , DL_Parakeet_1000km_th )  > Static_model_bioclim_balanced_results_Parakeet_1000km[3,2] )

Static_model_bioclim_balanced_Parakeet_gbm_global_th <- ( crop( Static_model_bioclim_balanced_Parakeet_gbm_global , DL_Parakeet_global_th )  > Static_model_bioclim_balanced_results_Parakeet_global[1,2] )
Static_model_bioclim_balanced_Parakeet_maxent_global_th <- ( crop( Static_model_bioclim_balanced_Parakeet_maxent_global , DL_Parakeet_global_th )  > Static_model_bioclim_balanced_results_Parakeet_global[2,2] )
Static_model_bioclim_balanced_Parakeet_rf_global_th <- ( crop( Static_model_bioclim_balanced_Parakeet_rf_global , DL_Parakeet_global_th )  > Static_model_bioclim_balanced_results_Parakeet_global[3,2] )

# Parakeet -  bioclim imbalanced
Static_model_bioclim_imbalanced_Parakeet_gbm_1000km_th <- ( crop( Static_model_bioclim_imbalanced_Parakeet_gbm_1000km , DL_Parakeet_1000km_th )  > Static_model_bioclim_imbalanced_results_Parakeet_1000km[1,2] )
Static_model_bioclim_imbalanced_Parakeet_maxent_1000km_th <- ( crop( Static_model_bioclim_imbalanced_Parakeet_maxent_1000km , DL_Parakeet_1000km_th )  > Static_model_bioclim_imbalanced_results_Parakeet_1000km[2,2] )
Static_model_bioclim_imbalanced_Parakeet_rf_1000km_th <- ( crop( Static_model_bioclim_imbalanced_Parakeet_rf_1000km , DL_Parakeet_1000km_th )  > Static_model_bioclim_imbalanced_results_Parakeet_1000km[3,2] )

Static_model_bioclim_imbalanced_Parakeet_gbm_global_th <- ( crop( Static_model_bioclim_imbalanced_Parakeet_gbm_global , DL_Parakeet_global_th )  > Static_model_bioclim_imbalanced_results_Parakeet_global[1,2] )
Static_model_bioclim_imbalanced_Parakeet_maxent_global_th <- ( crop( Static_model_bioclim_imbalanced_Parakeet_maxent_global , DL_Parakeet_global_th )  > Static_model_bioclim_imbalanced_results_Parakeet_global[2,2] )
Static_model_bioclim_imbalanced_Parakeet_rf_global_th <- ( crop( Static_model_bioclim_imbalanced_Parakeet_rf_global , DL_Parakeet_global_th )  > Static_model_bioclim_imbalanced_results_Parakeet_global[3,2] )

# Parakeet -  worldclim balanced
Static_model_worldclim_balanced_Parakeet_gbm_1000km_th <- ( crop( Static_model_worldclim_balanced_Parakeet_gbm_1000km , DL_Parakeet_1000km_th )  > Static_model_worldclim_balanced_results_Parakeet_1000km[1,2] )
Static_model_worldclim_balanced_Parakeet_maxent_1000km_th <- ( crop( Static_model_worldclim_balanced_Parakeet_maxent_1000km , DL_Parakeet_1000km_th )  > Static_model_worldclim_balanced_results_Parakeet_1000km[2,2] )
Static_model_worldclim_balanced_Parakeet_rf_1000km_th <- ( crop( Static_model_worldclim_balanced_Parakeet_rf_1000km , DL_Parakeet_1000km_th )  > Static_model_worldclim_balanced_results_Parakeet_1000km[3,2] )

Static_model_worldclim_balanced_Parakeet_gbm_global_th <- ( crop( Static_model_worldclim_balanced_Parakeet_gbm_global , DL_Parakeet_global_th )  > Static_model_worldclim_balanced_results_Parakeet_global[1,2] )
Static_model_worldclim_balanced_Parakeet_maxent_global_th <- ( crop( Static_model_worldclim_balanced_Parakeet_maxent_global , DL_Parakeet_global_th )  > Static_model_worldclim_balanced_results_Parakeet_global[2,2] )
Static_model_worldclim_balanced_Parakeet_rf_global_th <- ( crop( Static_model_worldclim_balanced_Parakeet_rf_global , DL_Parakeet_global_th )  > Static_model_worldclim_balanced_results_Parakeet_global[3,2] )

#_________________________________________________________________________




```

#### 1000km {.tabset .tabset-pills}

##### Boar {.tabset .tabset-pills}

###### Bio_bal
```{r echo=FALSE}

plot( DL_Boar_1000km_th + Static_model_bioclim_balanced_Boar_gbm_1000km_th , main = "Boar - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "GBM" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Boar_1000km_th + Static_model_bioclim_balanced_Boar_maxent_1000km_th , main = "Boar - MaxEnt " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "MaxEnt" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Boar_1000km_th + Static_model_bioclim_balanced_Boar_rf_1000km_th , main = "Boar - RF " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "RF" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

```

###### Bio_imbal
```{r echo=FALSE}

plot( DL_Boar_1000km_th + Static_model_bioclim_imbalanced_Boar_gbm_1000km_th , main = "Boar - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "GBM" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Boar_1000km_th + Static_model_bioclim_imbalanced_Boar_maxent_1000km_th , main = "Boar - MaxEnt " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "MaxEnt" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Boar_1000km_th + Static_model_bioclim_imbalanced_Boar_rf_1000km_th , main = "Boar - RF " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "RF" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )


```

###### WC_bal
```{r echo=FALSE}

plot( DL_Boar_1000km_th + Static_model_worldclim_balanced_Boar_gbm_1000km_th , main = "Boar - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "GBM" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Boar_1000km_th + Static_model_worldclim_balanced_Boar_maxent_1000km_th , main = "Boar - MaxEnt " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "MaxEnt" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Boar_1000km_th + Static_model_worldclim_balanced_Boar_rf_1000km_th , main = "Boar - RF " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "RF" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )


```

##### Kudzu {.tabset .tabset-pills}

###### Bio_bal
```{r echo=FALSE}

plot( DL_Kudzu_1000km_th + Static_model_bioclim_balanced_Kudzu_gbm_1000km_th , main = "Kudzu - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "GBM" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Kudzu_1000km_th + Static_model_bioclim_balanced_Kudzu_maxent_1000km_th , main = "Kudzu - MaxEnt " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "MaxEnt" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Kudzu_1000km_th + Static_model_bioclim_balanced_Kudzu_rf_1000km_th , main = "Kudzu - RF " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "RF" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

```

###### Bio_imbal
```{r echo=FALSE}

plot( DL_Kudzu_1000km_th + Static_model_bioclim_imbalanced_Kudzu_gbm_1000km_th , main = "Kudzu - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "GBM" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Kudzu_1000km_th + Static_model_bioclim_imbalanced_Kudzu_maxent_1000km_th , main = "Kudzu - MaxEnt " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "MaxEnt" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Kudzu_1000km_th + Static_model_bioclim_imbalanced_Kudzu_rf_1000km_th , main = "Kudzu - RF " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "RF" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )


```

###### WC_bal
```{r echo=FALSE}

plot( DL_Kudzu_1000km_th + Static_model_worldclim_balanced_Kudzu_gbm_1000km_th , main = "Kudzu - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "GBM" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Kudzu_1000km_th + Static_model_worldclim_balanced_Kudzu_maxent_1000km_th , main = "Kudzu - MaxEnt " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "MaxEnt" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Kudzu_1000km_th + Static_model_worldclim_balanced_Kudzu_rf_1000km_th , main = "Kudzu - RF " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "RF" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )


```


##### Ladybird {.tabset .tabset-pills}

###### Bio_bal
```{r echo=FALSE}

plot( DL_Ladybird_1000km_th + Static_model_bioclim_balanced_Ladybird_gbm_1000km_th , main = "Ladybird - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "GBM" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Ladybird_1000km_th + Static_model_bioclim_balanced_Ladybird_maxent_1000km_th , main = "Ladybird - MaxEnt " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "MaxEnt" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Ladybird_1000km_th + Static_model_bioclim_balanced_Ladybird_rf_1000km_th , main = "Ladybird - RF " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "RF" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

```

###### Bio_imbal
```{r echo=FALSE}

plot( DL_Ladybird_1000km_th + Static_model_bioclim_imbalanced_Ladybird_gbm_1000km_th , main = "Ladybird - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "GBM" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Ladybird_1000km_th + Static_model_bioclim_imbalanced_Ladybird_maxent_1000km_th , main = "Ladybird - MaxEnt " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "MaxEnt" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Ladybird_1000km_th + Static_model_bioclim_imbalanced_Ladybird_rf_1000km_th , main = "Ladybird - RF " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "RF" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )


```

###### WC_bal
```{r echo=FALSE}

plot( DL_Ladybird_1000km_th + Static_model_worldclim_balanced_Ladybird_gbm_1000km_th , main = "Ladybird - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "GBM" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Ladybird_1000km_th + Static_model_worldclim_balanced_Ladybird_maxent_1000km_th , main = "Ladybird - MaxEnt " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "MaxEnt" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Ladybird_1000km_th + Static_model_worldclim_balanced_Ladybird_rf_1000km_th , main = "Ladybird - RF " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "RF" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )


```


##### Parakeet {.tabset .tabset-pills}

###### Bio_bal
```{r echo=FALSE}

plot( DL_Parakeet_1000km_th + Static_model_bioclim_balanced_Parakeet_gbm_1000km_th , main = "Parakeet - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "GBM" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Parakeet_1000km_th + Static_model_bioclim_balanced_Parakeet_maxent_1000km_th , main = "Parakeet - MaxEnt " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "MaxEnt" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Parakeet_1000km_th + Static_model_bioclim_balanced_Parakeet_rf_1000km_th , main = "Parakeet - RF " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "RF" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

```

###### Bio_imbal
```{r echo=FALSE}

plot( DL_Parakeet_1000km_th + Static_model_bioclim_imbalanced_Parakeet_gbm_1000km_th , main = "Parakeet - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "GBM" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Parakeet_1000km_th + Static_model_bioclim_imbalanced_Parakeet_maxent_1000km_th , main = "Parakeet - MaxEnt " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "MaxEnt" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Parakeet_1000km_th + Static_model_bioclim_imbalanced_Parakeet_rf_1000km_th , main = "Parakeet - RF " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "RF" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )


```

###### WC_bal
```{r echo=FALSE}

plot( DL_Parakeet_1000km_th + Static_model_worldclim_balanced_Parakeet_gbm_1000km_th , main = "Parakeet - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "GBM" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Parakeet_1000km_th + Static_model_worldclim_balanced_Parakeet_maxent_1000km_th , main = "Parakeet - MaxEnt " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "MaxEnt" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Parakeet_1000km_th + Static_model_worldclim_balanced_Parakeet_rf_1000km_th , main = "Parakeet - RF " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "RF" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )


```

#### {-}


#### Global {.tabset .tabset-pills}

##### Boar {.tabset .tabset-pills}

###### Bio_bal
```{r echo=FALSE}

plot( DL_Boar_global_th + Static_model_bioclim_balanced_Boar_gbm_global_th , main = "Boar - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "GBM" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Boar_global_th + Static_model_bioclim_balanced_Boar_maxent_global_th , main = "Boar - MaxEnt " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "MaxEnt" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Boar_global_th + Static_model_bioclim_balanced_Boar_rf_global_th , main = "Boar - RF " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "RF" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

```

###### Bio_imbal
```{r echo=FALSE}

plot( DL_Boar_global_th + Static_model_bioclim_imbalanced_Boar_gbm_global_th , main = "Boar - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "GBM" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Boar_global_th + Static_model_bioclim_imbalanced_Boar_maxent_global_th , main = "Boar - MaxEnt " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "MaxEnt" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Boar_global_th + Static_model_bioclim_imbalanced_Boar_rf_global_th , main = "Boar - RF " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "RF" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )


```

###### WC_bal
```{r echo=FALSE}

plot( DL_Boar_global_th + Static_model_worldclim_balanced_Boar_gbm_global_th , main = "Boar - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "GBM" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Boar_global_th + Static_model_worldclim_balanced_Boar_maxent_global_th , main = "Boar - MaxEnt " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "MaxEnt" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Boar_global_th + Static_model_worldclim_balanced_Boar_rf_global_th , main = "Boar - RF " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "RF" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )


```

##### Kudzu {.tabset .tabset-pills}

###### Bio_bal
```{r echo=FALSE}

plot( DL_Kudzu_global_th + Static_model_bioclim_balanced_Kudzu_gbm_global_th , main = "Kudzu - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "GBM" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Kudzu_global_th + Static_model_bioclim_balanced_Kudzu_maxent_global_th , main = "Kudzu - MaxEnt " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "MaxEnt" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Kudzu_global_th + Static_model_bioclim_balanced_Kudzu_rf_global_th , main = "Kudzu - RF " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "RF" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

```

###### Bio_imbal
```{r echo=FALSE}

plot( DL_Kudzu_global_th + Static_model_bioclim_imbalanced_Kudzu_gbm_global_th , main = "Kudzu - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "GBM" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Kudzu_global_th + Static_model_bioclim_imbalanced_Kudzu_maxent_global_th , main = "Kudzu - MaxEnt " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "MaxEnt" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Kudzu_global_th + Static_model_bioclim_imbalanced_Kudzu_rf_global_th , main = "Kudzu - RF " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "RF" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )


```

###### WC_bal
```{r echo=FALSE}

plot( DL_Kudzu_global_th + Static_model_worldclim_balanced_Kudzu_gbm_global_th , main = "Kudzu - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "GBM" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Kudzu_global_th + Static_model_worldclim_balanced_Kudzu_maxent_global_th , main = "Kudzu - MaxEnt " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "MaxEnt" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Kudzu_global_th + Static_model_worldclim_balanced_Kudzu_rf_global_th , main = "Kudzu - RF " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "RF" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )


```


##### Ladybird {.tabset .tabset-pills}

###### Bio_bal
```{r echo=FALSE}

plot( DL_Ladybird_global_th + Static_model_bioclim_balanced_Ladybird_gbm_global_th , main = "Ladybird - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "GBM" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Ladybird_global_th + Static_model_bioclim_balanced_Ladybird_maxent_global_th , main = "Ladybird - MaxEnt " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "MaxEnt" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Ladybird_global_th + Static_model_bioclim_balanced_Ladybird_rf_global_th , main = "Ladybird - RF " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "RF" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

```

###### Bio_imbal
```{r echo=FALSE}

plot( DL_Ladybird_global_th + Static_model_bioclim_imbalanced_Ladybird_gbm_global_th , main = "Ladybird - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "GBM" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Ladybird_global_th + Static_model_bioclim_imbalanced_Ladybird_maxent_global_th , main = "Ladybird - MaxEnt " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "MaxEnt" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Ladybird_global_th + Static_model_bioclim_imbalanced_Ladybird_rf_global_th , main = "Ladybird - RF " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "RF" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )


```

###### WC_bal
```{r echo=FALSE}

plot( DL_Ladybird_global_th + Static_model_worldclim_balanced_Ladybird_gbm_global_th , main = "Ladybird - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "GBM" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Ladybird_global_th + Static_model_worldclim_balanced_Ladybird_maxent_global_th , main = "Ladybird - MaxEnt " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "MaxEnt" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Ladybird_global_th + Static_model_worldclim_balanced_Ladybird_rf_global_th , main = "Ladybird - RF " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "RF" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )


```


##### Parakeet {.tabset .tabset-pills}

###### Bio_bal
```{r echo=FALSE}

plot( DL_Parakeet_global_th + Static_model_bioclim_balanced_Parakeet_gbm_global_th , main = "Parakeet - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "GBM" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Parakeet_global_th + Static_model_bioclim_balanced_Parakeet_maxent_global_th , main = "Parakeet - MaxEnt " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "MaxEnt" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Parakeet_global_th + Static_model_bioclim_balanced_Parakeet_rf_global_th , main = "Parakeet - RF " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "RF" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

```

###### Bio_imbal
```{r echo=FALSE}

plot( DL_Parakeet_global_th + Static_model_bioclim_imbalanced_Parakeet_gbm_global_th , main = "Parakeet - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "GBM" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Parakeet_global_th + Static_model_bioclim_imbalanced_Parakeet_maxent_global_th , main = "Parakeet - MaxEnt " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "MaxEnt" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Parakeet_global_th + Static_model_bioclim_imbalanced_Parakeet_rf_global_th , main = "Parakeet - RF " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "RF" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )


```

###### WC_bal
```{r echo=FALSE}

plot( DL_Parakeet_global_th + Static_model_worldclim_balanced_Parakeet_gbm_global_th , main = "Parakeet - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "GBM" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Parakeet_global_th + Static_model_worldclim_balanced_Parakeet_maxent_global_th , main = "Parakeet - MaxEnt " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "MaxEnt" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Parakeet_global_th + Static_model_worldclim_balanced_Parakeet_rf_global_th , main = "Parakeet - RF " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "RF" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )


```

#### {-}

#### P/A {.tabset .tabset-pills}

```{r include=FALSE}

# Monkeyflower

# Threshold finder

final_Monkeyflower_donut <- roc( data.frame( read_csv( "./Results_deep_learning/Best_models/Time_series_best_model_true_values_Monkeyflower.csv" ,  col_names = FALSE ) )$X1 , 
                          data.frame( read_csv( "./Results_deep_learning/Best_models/Time_series_best_model_test_predictions_Monkeyflower.csv",  col_names = FALSE ) )$X1 ) 
# Calculate sens_spec
# determine the best threshold
Monkeyflower_dl_th_donut <- which(final_Monkeyflower_donut$sensitivities + final_Monkeyflower_donut$specificities == max(final_Monkeyflower_donut$sensitivities + final_Monkeyflower_donut$specificities), arr.ind = TRUE)
final_Monkeyflower_donut$thresholds[[Monkeyflower_dl_th_donut]]


DL_Monkeyflower_donut_th <-  ( ( DL_Monkeyflower_donut > final_Monkeyflower_donut$thresholds[[Monkeyflower_dl_th_donut]] ) * 2 )

# Static models

# Monkeyflower -  bioclim balanced

Static_model_bioclim_balanced_Monkeyflower_gbm_donut_th <- ( crop( Static_model_bioclim_balanced_Monkeyflower_gbm_donut , DL_Monkeyflower_donut_th )  > Static_model_bioclim_balanced_results_Monkeyflower_donut[1,2] )
Static_model_bioclim_balanced_Monkeyflower_maxent_donut_th <- ( crop( Static_model_bioclim_balanced_Monkeyflower_maxent_donut , DL_Monkeyflower_donut_th )  > Static_model_bioclim_balanced_results_Monkeyflower_donut[2,2] )
Static_model_bioclim_balanced_Monkeyflower_rf_donut_th <- ( crop( Static_model_bioclim_balanced_Monkeyflower_rf_donut , DL_Monkeyflower_donut_th )  > Static_model_bioclim_balanced_results_Monkeyflower_donut[3,2] )

# Monkeyflower -  bioclim imbalanced

Static_model_bioclim_imbalanced_Monkeyflower_gbm_donut_th <- ( crop( Static_model_bioclim_imbalanced_Monkeyflower_gbm_donut , DL_Monkeyflower_donut_th )  > Static_model_bioclim_imbalanced_results_Monkeyflower_donut[1,2] )
Static_model_bioclim_imbalanced_Monkeyflower_maxent_donut_th <- ( crop( Static_model_bioclim_imbalanced_Monkeyflower_maxent_donut , DL_Monkeyflower_donut_th )  > Static_model_bioclim_imbalanced_results_Monkeyflower_donut[2,2] )
Static_model_bioclim_imbalanced_Monkeyflower_rf_donut_th <- ( crop( Static_model_bioclim_imbalanced_Monkeyflower_rf_donut , DL_Monkeyflower_donut_th )  > Static_model_bioclim_imbalanced_results_Monkeyflower_donut[3,2] )

# Monkeyflower -  worldclim balanced

Static_model_worldclim_balanced_Monkeyflower_gbm_donut_th <- ( crop( Static_model_worldclim_balanced_Monkeyflower_gbm_donut , DL_Monkeyflower_donut_th )  > Static_model_worldclim_balanced_results_Monkeyflower_donut[1,2] )
Static_model_worldclim_balanced_Monkeyflower_maxent_donut_th <- ( crop( Static_model_worldclim_balanced_Monkeyflower_maxent_donut , DL_Monkeyflower_donut_th )  > Static_model_worldclim_balanced_results_Monkeyflower_donut[2,2] )
Static_model_worldclim_balanced_Monkeyflower_rf_donut_th <- ( crop( Static_model_worldclim_balanced_Monkeyflower_rf_donut , DL_Monkeyflower_donut_th )  > Static_model_worldclim_balanced_results_Monkeyflower_donut[3,2] )




```



##### Bio_bal
```{r echo=FALSE}

plot( DL_Monkeyflower_donut_th + Static_model_bioclim_balanced_Monkeyflower_gbm_donut_th , main = "Monkeyflower - GBM " , 
      legend = FALSE , xlim = c( -125.156250 , -110.917969 ) , ylim = c( 32.287133 , 49.439557 ) ,
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) ,  
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "GBM" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Monkeyflower_donut_th + Static_model_bioclim_balanced_Monkeyflower_maxent_donut_th , main = "Monkeyflower - MaxEnt " , 
      legend = FALSE , xlim = c( -125.156250 , -110.917969 ) , ylim = c( 32.287133 , 49.439557 ) ,
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "MaxEnt" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Monkeyflower_donut_th + Static_model_bioclim_balanced_Monkeyflower_rf_donut_th , main = "Monkeyflower - RF " , 
      legend = FALSE , xlim = c( -125.156250 , -110.917969 ) , ylim = c( 32.287133 , 49.439557 ) ,
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "RF" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

```

##### Bio_imbal
```{r echo=FALSE}

plot( DL_Monkeyflower_donut_th + Static_model_bioclim_imbalanced_Monkeyflower_gbm_donut_th , main = "Monkeyflower - GBM " , 
      legend = FALSE , xlim = c( -125.156250 , -110.917969 ) , ylim = c( 32.287133 , 49.439557 ) ,
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "GBM" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Monkeyflower_donut_th + Static_model_bioclim_imbalanced_Monkeyflower_maxent_donut_th , main = "Monkeyflower - MaxEnt " , 
      legend = FALSE , xlim = c( -125.156250 , -110.917969 ) , ylim = c( 32.287133 , 49.439557 ) ,
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "MaxEnt" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Monkeyflower_donut_th + Static_model_bioclim_imbalanced_Monkeyflower_rf_donut_th , main = "Monkeyflower - RF " , 
      legend = FALSE , xlim = c( -125.156250 , -110.917969 ) , ylim = c( 32.287133 , 49.439557 ) ,
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "RF" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )


```

##### WC_bal
```{r echo=FALSE}

plot( DL_Monkeyflower_donut_th + Static_model_worldclim_balanced_Monkeyflower_gbm_donut_th , main = "Monkeyflower - GBM " , 
      legend = FALSE , xlim = c( -125.156250 , -110.917969 ) , ylim = c( 32.287133 , 49.439557 ) ,
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "GBM" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Monkeyflower_donut_th + Static_model_worldclim_balanced_Monkeyflower_maxent_donut_th , main = "Monkeyflower - MaxEnt " , 
      legend = FALSE , xlim = c( -125.156250 , -110.917969 ) , ylim = c( 32.287133 , 49.439557 ) ,
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "MaxEnt" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Monkeyflower_donut_th + Static_model_worldclim_balanced_Monkeyflower_rf_donut_th , main = "Monkeyflower - RF " , 
      legend = FALSE , xlim = c( -125.156250 , -110.917969 ) , ylim = c( 32.287133 , 49.439557 ) ,
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "DLNN" , "RF" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )


```


### {-}


### Prediction comparisons: 1000km buffer v. global buffer {.tabset .tabset-pills}

#### Boar {.tabset .tabset-pills}

##### DL
```{r echo=FALSE}

plot( 2*DL_Boar_1000km_th +  DL_Boar_global_th , main = "Boar - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Buffer" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

```


#####  Bio_bal
```{r echo=FALSE}

plot( Static_model_bioclim_balanced_Boar_gbm_1000km_th + Static_model_bioclim_balanced_Boar_gbm_global_th , main = "Boar - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( Static_model_bioclim_balanced_Boar_maxent_1000km_th + Static_model_bioclim_balanced_Boar_maxent_global_th , main = "Boar - MaxEnt " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( Static_model_bioclim_balanced_Boar_rf_1000km_th + Static_model_bioclim_balanced_Boar_rf_global_th , main = "Boar - RF " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

```

#####  Bio_imbal
```{r echo=FALSE}

plot( Static_model_bioclim_imbalanced_Boar_gbm_1000km_th + Static_model_bioclim_imbalanced_Boar_gbm_global_th , main = "Boar - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( Static_model_bioclim_imbalanced_Boar_maxent_1000km_th + Static_model_bioclim_imbalanced_Boar_maxent_global_th , main = "Boar - MaxEnt " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( DL_Boar_1000km_th + Static_model_bioclim_imbalanced_Boar_rf_global_th , main = "Boar - RF " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )


```

#####  WC_bal
```{r echo=FALSE}

plot( Static_model_worldclim_balanced_Boar_gbm_1000km_th + Static_model_worldclim_balanced_Boar_gbm_global_th , main = "Boar - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( Static_model_worldclim_balanced_Boar_maxent_1000km_th + Static_model_worldclim_balanced_Boar_maxent_global_th , main = "Boar - MaxEnt " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( Static_model_worldclim_balanced_Boar_rf_1000km_th + Static_model_worldclim_balanced_Boar_rf_global_th , main = "Boar - RF " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )


```

#### {-}

#### Kudzu {.tabset .tabset-pills}

##### DL
```{r echo=FALSE}

plot( 2*DL_Kudzu_1000km_th +  DL_Kudzu_global_th , main = "Kudzu - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Buffer" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

```

##### Bio_bal
```{r echo=FALSE}

plot( Static_model_bioclim_balanced_Kudzu_gbm_1000km_th + Static_model_bioclim_balanced_Kudzu_gbm_global_th , main = "Kudzu - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( Static_model_bioclim_balanced_Kudzu_maxent_1000km_th + Static_model_bioclim_balanced_Kudzu_maxent_global_th , main = "Kudzu - MaxEnt " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot(  Static_model_bioclim_balanced_Kudzu_rf_1000km_th + Static_model_bioclim_balanced_Kudzu_rf_global_th , main = "Kudzu - RF " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

```

##### Bio_imbal
```{r echo=FALSE}

plot( Static_model_bioclim_imbalanced_Kudzu_gbm_1000km_th + Static_model_bioclim_imbalanced_Kudzu_gbm_global_th , main = "Kudzu - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( Static_model_bioclim_imbalanced_Kudzu_maxent_1000km_th + Static_model_bioclim_imbalanced_Kudzu_maxent_global_th , main = "Kudzu - MaxEnt " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( Static_model_bioclim_imbalanced_Kudzu_rf_1000km_th + Static_model_bioclim_imbalanced_Kudzu_rf_global_th , main = "Kudzu - RF " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )


```

##### WC_bal
```{r echo=FALSE}

plot( Static_model_worldclim_balanced_Kudzu_gbm_1000km_th + Static_model_worldclim_balanced_Kudzu_gbm_global_th , main = "Kudzu - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( Static_model_worldclim_balanced_Kudzu_maxent_1000km_th + Static_model_worldclim_balanced_Kudzu_maxent_global_th , main = "Kudzu - MaxEnt " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( Static_model_worldclim_balanced_Kudzu_rf_1000km_th + Static_model_worldclim_balanced_Kudzu_rf_global_th , main = "Kudzu - RF " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )


```

#### {-}

#### Ladybird {.tabset .tabset-pills}

##### DL
```{r echo=FALSE}

plot( 2*DL_Ladybird_1000km_th +  DL_Ladybird_global_th , main = "Ladybird - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Buffer" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

```


#####Bio_bal
```{r echo=FALSE}

plot( Static_model_bioclim_balanced_Ladybird_gbm_1000km_th + Static_model_bioclim_balanced_Ladybird_gbm_global_th , main = "Ladybird - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( Static_model_bioclim_balanced_Ladybird_maxent_1000km_th + Static_model_bioclim_balanced_Ladybird_maxent_global_th , main = "Ladybird - MaxEnt " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( Static_model_bioclim_balanced_Ladybird_rf_1000km_th + Static_model_bioclim_balanced_Ladybird_rf_global_th , main = "Ladybird - RF " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

```

##### Bio_imbal
```{r echo=FALSE}

plot( Static_model_bioclim_imbalanced_Ladybird_gbm_1000km_th + Static_model_bioclim_imbalanced_Ladybird_gbm_global_th , main = "Ladybird - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( Static_model_bioclim_imbalanced_Ladybird_maxent_1000km_th + Static_model_bioclim_imbalanced_Ladybird_maxent_global_th , main = "Ladybird - MaxEnt " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( Static_model_bioclim_imbalanced_Ladybird_rf_1000km_th + Static_model_bioclim_imbalanced_Ladybird_rf_global_th , main = "Ladybird - RF " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )


```

##### WC_bal
```{r echo=FALSE}

plot( Static_model_worldclim_balanced_Ladybird_gbm_1000km_th + Static_model_worldclim_balanced_Ladybird_gbm_global_th , main = "Ladybird - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( Static_model_worldclim_balanced_Ladybird_maxent_1000km_th + Static_model_worldclim_balanced_Ladybird_maxent_global_th , main = "Ladybird - MaxEnt " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( Static_model_worldclim_balanced_Ladybird_rf_1000km_th  + Static_model_worldclim_balanced_Ladybird_rf_global_th , main = "Ladybird - RF " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )


```

#### {-}

#### Parakeet {.tabset .tabset-pills}

##### DL
```{r echo=FALSE}

plot( 2*DL_Parakeet_1000km_th +  DL_Parakeet_global_th , main = "Parakeet - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Buffer" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

```


##### Bio_bal
```{r echo=FALSE}

plot( Static_model_bioclim_balanced_Parakeet_gbm_1000km_th + Static_model_bioclim_balanced_Parakeet_gbm_global_th , main = "Parakeet - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( Static_model_bioclim_balanced_Parakeet_maxent_1000km_th + Static_model_bioclim_balanced_Parakeet_maxent_global_th , main = "Parakeet - MaxEnt " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( Static_model_bioclim_balanced_Parakeet_rf_1000km_th + Static_model_bioclim_balanced_Parakeet_rf_global_th , main = "Parakeet - RF " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

```

##### Bio_imbal
```{r echo=FALSE}

plot( Static_model_bioclim_imbalanced_Parakeet_gbm_1000km_th + Static_model_bioclim_imbalanced_Parakeet_gbm_global_th , main = "Parakeet - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( Static_model_bioclim_imbalanced_Parakeet_maxent_1000km_th + Static_model_bioclim_imbalanced_Parakeet_maxent_global_th , main = "Parakeet - MaxEnt " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( Static_model_bioclim_imbalanced_Parakeet_rf_1000km_th + Static_model_bioclim_imbalanced_Parakeet_rf_global_th , main = "Parakeet - RF " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )


```

##### WC_bal
```{r echo=FALSE}

plot( Static_model_worldclim_balanced_Parakeet_gbm_1000km_th + Static_model_worldclim_balanced_Parakeet_gbm_global_th , main = "Parakeet - GBM " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( Static_model_worldclim_balanced_Parakeet_maxent_1000km_th + Static_model_worldclim_balanced_Parakeet_maxent_global_th , main = "Parakeet - MaxEnt " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )

plot( Static_model_worldclim_balanced_Parakeet_rf_1000km_th + Static_model_worldclim_balanced_Parakeet_rf_global_th , main = "Parakeet - RF " , 
      legend = FALSE , 
      col = c("azure2" , "cornflowerblue" ,  "forestgreen", "goldenrod1" ) 
  )
legend( "bottomright" , 
       title = "Algorithm" , 
       c( "1000km" , "Global" , "Both" ) , 
       fill = c( "forestgreen", "cornflowerblue" , "goldenrod1") ,
       cex=0.6 )


```

#### {-}

### {-}


### References

* Angert, Amy L., Matthew Bayly, Seema N. Sheth, and John R. Paul. "Testing range-limit hypotheses using range-wide habitat suitability and occupancy for the scarlet monkeyflower (Erythranthe cardinalis)." The American Naturalist 191, no. 3 (2018): E76-E89.  https://doi.org/10.1086/695984

* Bidinger, Kerstin, S. Lötters, D. Rödder, and M. Veith. "Species distribution models for the alien invasive Asian Harlequin ladybird (Harmonia axyridis)." Journal of Applied Entomology 136, no. 1‐2 (2012): 109-123. https://doi.org/10.1111/j.1439-0418.2010.01598.x

* Bohl, Corentin L., Jamie M. Kass, and Robert P. Anderson. "A new null model approach to quantify performance and significance for ecological niche models of species distributions." Journal of Biogeography 46, no. 6 (2019): 1101-1111. https://doi.org/10.1111/jbi.13573

* Breiman, Leo. "Random forests." Machine learning 45, no. 1 (2001): 5-32. https://link.springer.com/article/10.1023/A:1010933404324

* Callen, Steven T., and Allison J. Miller. "Signatures of niche conservatism and niche shift in the North American kudzu (Pueraria montana) invasion." Diversity and Distributions 21, no. 8 (2015): 853-863. https://doi.org/10.1111/ddi.12341

* Capinha, César, Ana Ceia-Hasse, Andrew M. Kramer, and Christiaan Meijer. "Deep learning for supervised classification of temporal data in ecology." Ecological Informatics 61 (2021): 101252. https://doi.org/10.1016/j.ecoinf.2021.101252

* Cutler, D. Richard, Thomas C. Edwards Jr, Karen H. Beard, Adele Cutler, Kyle T. Hess, Jacob Gibson, and Joshua J. Lawler. "Random forests for classification in ecology." Ecology 88, no. 11 (2007): 2783-2792. https://doi.org/10.1890/07-0539.1

* De'Ath, Glenn. "Boosted trees for ecological modeling and prediction." Ecology 88, no. 1 (2007): 243-251.  https://doi.org/10.1890/0012-9658(2007)88[243:BTFEMA]2.0.CO;2

* Elith, Jane, John R. Leathwick, and Trevor Hastie. "A working guide to boosted regression trees." Journal of Animal Ecology 77, no. 4 (2008): 802-813. https://doi.org/10.1111/j.1365-2656.2008.01390.x

* Elith, Jane, and John R. Leathwick. "Species distribution models: ecological explanation and prediction across space and time." Annual review of ecology, evolution, and systematics 40 (2009): 677-697. https://doi.org/10.1146/annurev.ecolsys.110308.120159

* Elith, Jane, Steven J. Phillips, Trevor Hastie, Miroslav Dudík, Yung En Chee, and Colin J. Yates. "A statistical explanation of MaxEnt for ecologists." Diversity and distributions 17, no. 1 (2011): 43-57. https://doi.org/10.1111/j.1472-4642.2010.00725.x

* Evans, Jeffrey S., Melanie A. Murphy, Zachary A. Holden, and Samuel A. Cushman. "Modeling species distribution and change using random forest." In Predictive species and habitat modeling in landscape ecology, pp. 139-159. Springer, New York, NY, 2011. https://link.springer.com/chapter/10.1007/978-1-4419-7390-0_8

* Fick, Stephen E., and Robert J. Hijmans. "WorldClim 2: new 1‐km spatial resolution climate surfaces for global land areas." International journal of climatology 37, no. 12 (2017): 4302-4315. https://doi.org/10.1002/joc.5086

* Friedman, Jerome H. "Greedy function approximation: a gradient boosting machine." Annals of statistics (2001): 1189-1232. https://www.jstor.org/stable/2699986

* Guisan, Antoine, and Niklaus E. Zimmermann. "Predictive habitat distribution models in ecology." Ecological modelling 135, no. 2-3 (2000): 147-186. https://doi.org/10.1016/S0304-3800(00)00354-9

* Hastie, Trevor, Robert Tibshirani, and Jerome Friedman. The elements of statistical learning: data mining, inference, and prediction. Springer Science & Business Media, 2009.

* Hijmans, Robert J. "Cross‐validation of species distribution models: removing spatial sorting bias and calibration with a null model." Ecology 93, no. 3 (2012): 679-688. https://doi.org/10.1890/11-0826.1

* Hutchinson, G. E. "Concluding remarks". Cold Spring Harbor Symposia on Quantitative Biology 22 415–427 (1957) doi:10.1101/SQB.1957.022.01.039

* James, Gareth, Daniela Witten, Trevor Hastie, and Robert Tibshirani. An introduction to statistical learning. Vol. 112. New York: springer, 2013.

* Kuhn, Max, and Kjell Johnson. Applied predictive modeling. Vol. 26. New York: Springer, 2013.

* Liu, Canran, Graeme Newell, and Matt White. "On the selection of thresholds for predicting species occurrence with presence‐only data." Ecology and evolution 6, no. 1 (2016): 337-348. https://doi.org/10.1002/ece3.1878

* Milanesi, Pietro, Francesca Della Rocca, and Robert A. Robinson. "Integrating dynamic environmental predictors and species occurrences: Toward true dynamic species distribution models." Ecology and evolution 10, no. 2 (2020): 1087-1092. https://doi.org/10.1002/ece3.5938

* Norberg, Anna, Nerea Abrego, F. Guillaume Blanchet, Frederick R. Adler, Barbara J. Anderson, Jani Anttila, Miguel B. Araújo et al. "A comprehensive evaluation of predictive performance of 33 species distribution models at species and community levels." Ecological Monographs 89, no. 3 (2019): e01370. https://doi.org/10.1002/ecm.1370

* Pearson, R.G., Dawson, T.P., Berry, P.M. & Harrison, P.A. (2002) SPECIES: a spatial evaluation of climate impact on the envelope of species. Ecological Modelling, 154, 289–300. https://doi.org/10.1016/S0304-3800(02)00056-X

* Phillips, Steven J., Robert P. Anderson, and Robert E. Schapire. "Maximum entropy modeling of species geographic distributions." Ecological modelling 190, no. 3-4 (2006): 231-259. https://doi.org/10.1016/j.ecolmodel.2005.03.026

* Pearson, Richard G., and Terence P. Dawson. "Predicting the impacts of climate change on the distribution of species: are bioclimate envelope models useful?." Global ecology and biogeography 12, no. 5 (2003): 361-371. https://doi.org/10.1046/j.1466-822X.2003.00042.x

* Sales, Lilian Patrícia, Bruno R. Ribeiro, Matt Warrington Hayward, Adriano Paglia, Marcelo Passamani, and Rafael Loyola. "Niche conservatism and the invasive potential of the wild boar." Journal of Animal Ecology 86, no. 5 (2017): 1214-1223.  https://doi.org/10.1111/1365-2656.12721

* van Kuppevelt, D., C. Meijer, F. Huber, A. van der Ploeg, S. Georgievska, and V. T. van Hees. "Mcfly: Automated deep learning on time series." SoftwareX 12 (2020): 100548. https://doi.org/10.1016/j.softx.2020.100548



